title: "Appendix A - ADS506-01-FA22 - Final Project"
author: "Team 1"
date: "12/05/2022"
output:
  pdf_document: default
  html_document:
    df_print: paged
header-includes:
- \usepackage{fvextra}
- \DefineVerbatimEnvironment{Highlighting}{Verbatim}{breaklines,commandchars=\\\{\}}
- \usepackage{pdflscape}
- \newcommand{\blandscape}{\begin{landscape}}
- \newcommand{\elandscape}{\end{landscape}}
---

## RMarkdown global setup
```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

```{r global.options, include=TRUE}
knitr::opts_chunk$set(fig.align = 'center')
```

```{r lib, message=FALSE, warning=FALSE}
library(AppliedPredictiveModeling)
library(BioStatR)
library(car)
library(caret)
library(class)
library(corrplot)
library(datasets)
library(e1071)
library(Hmisc)
library(mlbench)
library(gridExtra)
library(psych)
library(randomForest)
library(RANN)
library(reshape2)
library(rpart)
library(rpart.plot)
library(scales)
library(tidyverse)
library(tseries)
library(zoo)

set.seed(1699)
```

## Create function to generate boxplots for continuous variables
```{r}
# Define function to produce formatted boxplots
box_comp <- function(xcol = c(), df = NA, rtn_met = TRUE) {
  sig <- 3
  metrics_df01 <- data.frame(metric = c("",
                                        "Total N:",
                                        "Count",
                                        "NA Count",
                                        "Mean",
                                        "Median",
                                        "Standard Deviation",
                                        "Variance",
                                        "Range",
                                        "Min",
                                        "Max",
                                        "25th Percentile",
                                        "75th Percentile",
                                        "Subset w/o Outliers:",
                                        "Count",
                                        "%",
                                        "Outlier %",
                                        "NA Count",
                                        "Mean",
                                        "Median",
                                        "Standard Deviation",
                                        "Variance",
                                        "Range",
                                        "Min",
                                        "Max"
                                        ))
  for (var in xcol) {
    df_s1 <- df[, var]
    df_s1s1 <-data.frame(df_s1)
    df_s1_fit <- preProcess(df_s1s1,
                            method = c("center", "scale"))
    df_s1_trans <- predict(df_s1_fit, df_s1s1)
    

    # Calculate quartiles
    var_iqr_lim <- IQR(df_s1) * 1.5
    var_q1 <- quantile(df_s1, probs = c(.25))
    var_otlow <- var_q1 - var_iqr_lim
    var_q3 <- quantile(df_s1, probs = c(.75))
    var_othigh <- var_q3 + var_iqr_lim
    
    # Subset non-outlier data 
    var_non_otlr_df01 <- subset(df, (abs(df_s1_trans) <= 3))
    #var_non_otlr_df01 <- subset(df, (df_s1 > var_otlow & df_s1 < var_othigh))
    df_s2 <- var_non_otlr_df01[, var]

    # Begin calculating measures of centrality & dispersion
    var_mean <- mean(df_s1)
    var_non_otlr_df01_trunc_mean <- mean(df_s2)
    var_med <- median(df_s1)
    var_non_otlr_df01_trunc_med <- median(df_s2)
    var_mode <- mode(df_s1)
    var_non_otlr_df01_trunc_mode <- mode(df_s2)
    var_stde <- sd(df_s1)
    var_non_otlr_df01_trunc_stde <- sd(df_s2)
    var_vari <- var(df_s1)
    var_non_otlr_df01_trunc_vari <- var(df_s2)
    var01_min <- min(df[, var])
    var01_max <- max(df[, var])
    var01_range <- var01_max - var01_min
    var02_min <- min(var_non_otlr_df01[, var])
    var02_max <- max(var_non_otlr_df01[, var])
    var02_range <- var02_max - var02_min
    
    # Configure y-axis min & max to sync graphs
    plot_min <- min(var01_min, var02_min)
    plot_max <- max(var01_max, var02_max)
    nonoutlier_perc <- round((as.numeric(dim(var_non_otlr_df01)[1] / as.numeric(dim(df)[1]))) * 100, 1)
    measure_val01 <- c(paste0("Variable: ", var),
                       "",
                       as.character(dim(df)[1]),
                       sum(is.na(df_s1)),
                       round(var_mean, sig),
                       round(var_med, sig),
                       round(var_stde, sig),
                       round(var_vari, sig),
                       round(var01_range, sig),
                       round(var01_min, sig),
                       round(var01_max, sig),
                       round(var_q1, sig),
                       round(var_q3, sig),
                       "",
                       as.character(dim(var_non_otlr_df01)[1]),
                       paste0(nonoutlier_perc, "%"),
                       paste0(round(100 - nonoutlier_perc, 1), "%"),
                       sum(is.na(df_s2)),
                       round(var_non_otlr_df01_trunc_mean, sig),
                       round(var_non_otlr_df01_trunc_med, sig),
                       round(var_non_otlr_df01_trunc_stde, sig),
                       round(var_non_otlr_df01_trunc_vari, sig),
                       round(var02_range, sig),
                       round(var02_min, sig),
                       round(var02_max, sig)
                       )
    
    var_name <- paste0("Variable: ", var)
    metrics_df01[, ncol(metrics_df01) + 1] <- measure_val01
}
  boxplot(df)
  if(rtn_met == TRUE) {
    return(metrics_df01)
  }
}
```

## Importing Train/Test Datasets
```{r}
# Import 4 separate CSV fukes
setwd('C:/Users/Connie/Documents/Masters Applied Data Science USD/506/Week2/Final Project/Ocean WAter')

owt_df01a <- read_csv("water_quality_1990_1999_datasd.csv", col_types = cols(date_sample=col_date("%Y-%m-%d")))
owt_df01b <- read_csv("water_quality_2000_2010_datasd.csv", col_types = cols(date_sample=col_date("%Y-%m-%d")))
owt_df01c <- read_csv("water_quality_2011_2019_datasd.csv", col_types = cols(date_sample=col_date("%Y-%m-%d")))
owt_df01d <- read_csv("water_quality_2020_2021_datasd.csv", col_types = cols(date_sample=col_date("%Y-%m-%d")))


# Merge 4 separate dataframes into 1
owt_df01 <- rbind(owt_df01a, owt_df01b, owt_df01c, owt_df01d)

# Bin the depth column by normal distribution cut offs
owt_df01$bin_depth <- cut(owt_df01$depth_m, breaks=c(0,8,33,47,70,90,112))
# labels=c("1-4","5-10","10-15")

# (CC) Split merged dataset into separate dataframes by PLOO and SBOO projects
df_ploo <- owt_df01[ which(owt_df01$project=='PLOO'), ]
df_sboo <- owt_df01[ which(owt_df01$project=='SBOO'), ]

print(head(owt_df01))
describe(owt_df01)

#write.csv(owt_df01, "../data/Ocean Water/ocean_df01.csv")
```


```{r CC-EDA-TrendSeasonality-1Year-PLOO1991}

# TIME SERIES PLOTS FOR PLOO PROJECT
plot_1991_parameters <- function(df_data) {
  
  # Get number of parameters
  params <- unique(df_data$parameter)
  numCats <- length(params)
  
  # Plot time series for each parameter: ENTERO, PH, SALINITY etc.
  for (param in params)
  {
     #print("param = ")
     #print(param)
     
     # Plot for One Year in Dataset PLOO - 1991
     df_param <- subset(df_data, format(as.Date(date_sample),"%Y")==1991 & df_data$parameter == param,)
      
     # if no data, then skip to next parameter
     if (dim(df_param)[1] == 0) {
       #print(dim(df_param))
       next
     }
     
     # take the mean of all station values for that date
     df_param <- aggregate(x = df_param$value, by = list(df_param$date_sample), FUN = mean)
     
     # cut out outliers
     df_param <- df_param[df_param$x < 6000, ]
    
     # ts_param <- ts(df_param$x, start = c(1991, 1), freq = 365)

     # https://koalatea.io/r-plot-timeseries/
     print(ggplot(df_param, aes(x = Group.1, y = x)) +
       geom_line() +
       theme(axis.text.x = element_text(angle = 45, hjust = 1))+
       scale_x_date(date_labels = "%Y-%b") +ggtitle(paste0("plot - PLOO - all depths - ",param)))
     
  }
    
}

plot_1991_parameters(df_ploo)

```



```{r CC-EDA-TrendSeasonality-1YearSBOO}

# 1 YEAR TIME SERIES FOR SBOO PROJECT ALL DEPTHS

plot_sboo_1999_parameters <- function(df_data) {
  
  # Get number of parameters
  params <- unique(df_data$parameter)
  numCats <- length(params)
  
  # Plot time series for each parameter: ENTERO, PH, SALINITY etc.
  for (param in params)
  {
     #print("param = ")
     #print(param)
     
     # Plot for One Year in Dataset - 1999
     df_param <- subset(df_data, format(as.Date(date_sample),"%Y")==1999 & df_data$parameter == param,)
     
     #print(colnames(df_param))
     #print(as.data.frame(table(df_param$bin_depth)))
       
     if (dim(df_param)[1] == 0) {
       print(dim(df_param))
       next
     }
     
     df_param <- aggregate(x = df_param$value, by = list(df_param$date_sample), FUN = mean)
    df_param <- df_param[df_param$x < 6000, ]
    #ts_param <- ts(df_param$x, start = c(1991, 1), freq = 365)

    # https://koalatea.io/r-plot-timeseries/
    print(ggplot(df_param, aes(x = Group.1, y = x)) +
       geom_line() +
       theme(axis.text.x = element_text(angle = 45, hjust = 1))+
       scale_x_date(date_labels = "%Y-%b") +ggtitle(paste0("plot - 1999 - SBOO - all depths - ",param)))
     
  }
    
}

plot_sboo_1999_parameters(df_sboo)
```



```{r CC-EDA-TrendSeasonality-PLOO-5Years}

# TIMES SERIES for PLOO 5 YEARS 1991 - 1996

plot_5years_parameters <- function(df_data) {
  
  # Get number of parameters
  params <- unique(df_data$parameter)
  numCats <- length(params)
  
  # Plot time series for each parameter: ENTERO, PH, SALINITY etc.
  for (param in params)
  {
     #print("param = ")
     print(param)
     
     # Get rows between 1991 - 1996
     df_param <- subset(df_data, format(as.Date(date_sample),"%Y")> 1997 & format(as.Date(date_sample),"%Y") < 2003 & df_data$parameter == param,)
     
     #print(colnames(df_param))
     #print(as.data.frame(table(df_param$bin_depth)))
       
     if (dim(df_param)[1] == 0) {
       next
     }
     
     df_param <- aggregate(x = df_param$value, by = list(df_param$date_sample), FUN = mean)
    df_param <- df_param[df_param$x < 6000, ]
    #ts_param <- ts(df_param$x, start = c(1991, 1), freq = 365)

    # https://koalatea.io/r-plot-timeseries/
    print(ggplot(df_param, aes(x = Group.1, y = x)) +
       geom_line() +
       theme(axis.text.x = element_text(angle = 45, hjust = 1))+
       scale_x_date(date_labels = "%Y-%b") +ggtitle(paste0("PLOO - 1991-1996 - all depths - ",param)))
     
  }
    
}

plot_5years_parameters(df_ploo)

```
```{r CC-EDA-TrendSeasonality-SBOO-5Years}
plot_5years_parameters(df_sboo)
```


```{r CC-EDA-TrendSeasonality-weekmonth-CHECK}
# ENTERO
# By Range 1 Week
# https://stackoverflow.com/questions/22439540/how-to-get-week-numbers-from-dates

df_ploo_1mon_entero <- subset(df_ploo, format(as.Date(date_sample),"%Y-%m")=='1991-01' & df_ploo$parameter == "ENTERO",)

#out <- strftime(df_ploo_1mon_entero$date_sample, format = "%V")

df_ploo_1mon_entero <- aggregate(x = df_ploo_1mon_entero$value, by = list(df_ploo_1mon_entero$date_sample), FUN = mean)

# Find the outlier value and remove it
hist(df_ploo_1mon_entero$x, main = "Histogram of Averaged Values over All Stations and Depths in 1 week in January 1991")

df_ploo_1mon_entero <- df_ploo_1mon_entero[df_ploo_1mon_entero$x < 6000, ]

ts_ploo_1mon_entero <- ts(df_ploo_1mon_entero$x, start = c(1991, 1), freq = 365)

plot(ts_ploo_1mon_entero,
     xlab = "Time",
     ylab = "Entero Levels",
     type = "o",
     main = "Figure 1. Entero Levels Over 1 Week (1991)")
grid()

# https://koalatea.io/r-plot-timeseries/
ggplot(df_ploo_1mon_entero, aes(x = Group.1, y = x)) +
       geom_line() +
   theme(axis.text.x = element_text(angle = 45, hjust = 1))+
       scale_x_date(date_labels = "%Y-%b-%d", breaks = date_breaks("1 day"))


# By Range 1 Month - Jan 1991
df_ploo_1mon_entero <- subset(df_ploo, format(as.Date(date_sample),"%Y-%m")=='1991-01' & df_ploo$parameter == "ENTERO",)

df_ploo_1mon_entero <- aggregate(x = df_ploo_1mon_entero$value, by = list(df_ploo_1mon_entero$date_sample), FUN = mean)

# Find the outlier value and remove it
hist(df_ploo_1mon_entero$x, main = "Histogram of Averaged Values over All Stations and Depths in January 1991")

df_ploo_1mon_entero <- df_ploo_1mon_entero[df_ploo_1mon_entero$x < 6000, ]

ts_ploo_1mon_entero <- ts(df_ploo_1mon_entero$x, start = c(1991, 1), freq = 365)

# https://koalatea.io/r-plot-timeseries/
ggplot(df_ploo_1mon_entero, aes(x = Group.1, y = x)) +
       geom_line() +
   theme(axis.text.x = element_text(angle = 45, hjust = 1))+
       scale_x_date(date_labels = "%Y-%b-%d", breaks = date_breaks("1 day"))

```



```{r CC-EDA-TrendSeasonality-1year-CHECK}
# By Range 1 Year
df_ploo_1yr_entero <- subset(df_ploo, format(as.Date(date_sample),"%Y")==1991 & df_ploo$parameter == "ENTERO",)

df_ploo_1yr_entero <- aggregate(x = df_ploo_1yr_entero$value, by = list(df_ploo_1yr_entero$date_sample), FUN = mean)

# Find the outlier value and remove it
hist(df_ploo_1yr_entero$x, main = "Histogram of Averaged Values over All Stations and Depths")

df_ploo_1yr_entero <- df_ploo_1yr_entero[df_ploo_1yr_entero$x < 6000, ]

ts_ploo_1yr_entero <- ts(df_ploo_1yr_entero$x, start = c(1991, 1), freq = 365)

plot(ts_ploo_1yr_entero,
     xlab = "Time",
     ylab = "Entero Levels",
     type = "o",
     main = "Figure 1. Entero Levels Over 1 Year (1991)")
grid()

# https://koalatea.io/r-plot-timeseries/
ggplot(df_ploo_1yr_entero, aes(x = Group.1, y = x)) +
       geom_line() +
   theme(axis.text.x = element_text(angle = 45, hjust = 1))+
       scale_x_date(date_labels = "%Y-%b", breaks = date_breaks("1 month"))
```


```{r CC-EDA-TrendSeasonality-PLOO-5years}
# https://joonim.medium.com/moving-to-tidy-forecasting-in-r-how-to-visualize-time-series-data-1d0e42aef11a

# Range for 5 years in dataset (1991 - 1996)
# decompose to detect seasonality
df_ploo_1991_1996_entero <- subset(df_ploo, format(as.Date(date_sample),"%Y")<= 1996 & df_ploo$parameter == "ENTERO" & df_ploo$value < 6000,)

df_ploo_1991_1996_entero <- aggregate(x = df_ploo_1991_1996_entero$value, by = list(df_ploo_1991_1996_entero$date_sample), FUN = mean)


library(ggplot2)

ggplot(df_ploo_1991_1996_entero, aes(x = Group.1, y = x)) +
       geom_line() +
   theme(axis.text.x = element_text(angle = 45, hjust = 1))+
       scale_x_date(date_labels = "%Y-%b-%d", breaks = date_breaks("1 months"))

#library(tibble)
#tb <- as_tibble(df_ploo_1991_1996_entero)
#ts_ploo_param <- ts(tb$x, start = c(1991,1), frequency = 365.25)

#ts_ploo_1991_1996_entero <- ts(df_ploo_1991_1996_entero$x, start = c(1991, 1), freq = 365)

#library(fpp3)
#library(feasts)
#tb %>% autoplot(tb)

#ts_ploo_param <- na.remove(ts_ploo_param)
#ts_comp_ploo_param <- decompose(ts_ploo_param)
#plot(ts_comp_ploo_param)
```
```{r CC-EDA-TrendSeasonality-SBOO-5years}
# Range for 5 years in dataset (1991 - 1996)
# decompose to detect seasonality
df_sboo_1991_1996_entero <- subset(df_sboo, format(as.Date(date_sample),"%Y")<= 2009 & df_sboo$parameter == "ENTERO" & df_sboo$value < 6000,)

#df_ploo_entero <- subset(df_ploo_1991_1996_entero, df_ploo_entero$x < 6000,)

df_sboo_1991_1996_entero <- aggregate(x = df_sboo_1991_1996_entero$value, by = list(df_sboo_1991_1996_entero$date_sample), FUN = mean)

ts_sboo_1991_1996_entero <- ts(df_sboo_1991_1996_entero$x, start = c(1991, 1), freq = 365)

ts_sboo_1991_1996_entero <- na.remove(ts_sboo_1991_1996_entero)
ts_comp_sboo_1991_1996_entero <- decompose(ts_sboo_1991_1996_entero)
plot(ts_comp_sboo_1991_1996_entero)
```

```{r CC-EDA-TrendSeasonality-allyears}
# Range for whole dataset in years
# decompose to detect seasonality
# https://stats.stackexchange.com/questions/346497/time-series-seasonality-test#:~:text=One%20of%20the%20most%20common,command%20from%20the%20forecast%20package.

plot_allyears_parameters <- function(df_data, dataset_name) {
  
  # Get number of parameters
  params <- unique(df_data$parameter)
  numCats <- length(params)
  
  # Plot time series for each parameter: ENTERO, PH, SALINITY etc.
  for (param in params)
  {
     print("param = ")
     print(param)
     
     df_param <- subset(df_data, df_data$parameter == param,)
     df_param <- subset(df_param, df_param$value < 6000,)
     df_param <- aggregate(x = df_param$value, by = list(df_param$date_sample), FUN = mean)

     ts_param <- ts(df_param$x, start = c(1991, 1), freq = 52)
     ts_param <- na.remove(ts_param)

     ts_comp_param <- decompose(ts_param)
     plot(ts_comp_param)
     mtext(param, side=3, line = -2)
     
  }
  
}

plot_allyears_parameters(df_ploo, "PLOO")
plot_allyears_parameters(df_sboo, "SBOO")

# Detecting cycles with Fourier Transform?
# https://stats.stackexchange.com/questions/217841/deseasonalizing-data-with-fourier-analysis
# https://medium.com/@khairulomar/deconstructing-time-series-using-fourier-transform-e52dd535a44e
# https://stackoverflow.com/questions/12330581/too-few-periods-for-decompose
# https://stats.stackexchange.com/questions/346497/time-series-seasonality-test#:~:text=One%20of%20the%20most%20common,command%20from%20the%20forecast%20package.
#https://stackoverflow.com/questions/15838533/rotating-axis-labels-in-date-format
# https://bookdown.dongzhuoer.com/hadley/ggplot2-book/date-time.html
# https://www.stat.berkeley.edu/~s133/dates.html
# https://koalatea.io/r-plot-timeseries/
# https://stackoverflow.com/questions/72049126/how-to-get-x-axis-to-show-all-months-in-dataset



```

```{r CC-EDA-TrendSeasonality-allyears}
# Range for whole dataset in years
# decompose to detect seasonality
# https://stats.stackexchange.com/questions/346497/time-series-seasonality-test#:~:text=One%20of%20the%20most%20common,command%20from%20the%20forecast%20package.
df_ploo_entero <- subset(df_ploo, df_ploo$parameter == "ENTERO",)

df_ploo_entero <- subset(df_ploo_entero, df_ploo_entero$value < 6000,)

df_ploo_entero <- aggregate(x = df_ploo_entero$value, by = list(df_ploo_entero$date_sample), FUN = mean)

ts_ploo_entero <- ts(df_ploo_entero$x, start = c(1991, 1), freq = 365)

ts_ploo_entero <- na.remove(ts_ploo_entero)

ts_comp_ploo_entero <- decompose(ts_ploo_entero)
plot(ts_comp_ploo_entero)

```


```{r CC-EDA-TrendSeasonality-SBOO-allyears}
# Range for whole dataset in years
# decompose to detect seasonality
# https://stats.stackexchange.com/questions/346497/time-series-seasonality-test#:~:text=One%20of%20the%20most%20common,command%20from%20the%20forecast%20package.
df_sboo_entero <- subset(df_sboo, df_sboo$parameter == "ENTERO",)

df_sboo_entero <- subset(df_sboo_entero, df_sboo_entero$value < 6000,)

df_sboo_entero <- aggregate(x = df_sboo_entero$value, by = list(df_sboo_entero$date_sample), FUN = mean)

ts_sboo_entero <- ts(df_sboo_entero$x, start = c(1991, 1), freq = 365)

ts_sboo_entero <- na.remove(ts_sboo_entero)

ts_comp_sboo_entero <- decompose(ts_sboo_entero)
plot(ts_comp_sboo_entero)

```

```{r CC-EDA-OutOfRangeValues}

# plot a bunch of histograms per parameter and per project

  params <- unique(df_ploo$parameter)
  numCats <- length(params)
  
  # Plot time series for each parameter: ENTERO, PH, SALINITY etc.
  for (param in params)
  {
     df_ploo_param <- subset(df_ploo, df_ploo$parameter == param,)
     hist(df_ploo_param$value, main = "Histogram of Values Per Parameter")
     mtext(param, side=3)
     #df_ploo_param <- df_ploo_param[df_ploo_param$value < 6000, ]
     
     # print out text range to output console
     r <- min(df_ploo_param$value, na.rm=TRUE)
     t <- max(df_ploo_param$value, na.rm=TRUE)
     writeLines(paste(param, " min: ", r))
     writeLines(paste(param, " max: ", t))
     # https://stackoverflow.com/questions/4716152/why-do-r-objects-not-print-in-a-function-or-a-for-loop
     #print(paste(param, " range: ", r)) 
  }


```
Output:
Lines marked ">>>>>>>>" are values that do not make sense:

CHLOROPHYLL  min:  -0.333
CHLOROPHYLL  max:  91.0317
DENSITY  min:  15.0254
DENSITY  max:  27.066
DO  min:  -9.99e-29>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>
DO  max:  89
PH  min:  7.124
PH  max:  8.727
SALINITY  min:  0>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>
SALINITY  max:  37.8
TEMP  min:  0>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>
TEMP  max:  25.54
XMS  min:  -37>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>
XMS  max:  95.41
ENTERO  min:  0>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>
ENTERO  max:  29000
FECAL  min:  0>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>
FECAL  max:  77000
TOTAL  min:  0>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>
TOTAL  max:  1100000>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>
OG  min:  0.2
OG  max:  0.955
SUSO  min:  0.2
SUSO  max:  84.9


```{r}
# Display aggregations by different features
owt_df01_gb01 <- owt_df01 %>%
  group_by(station) %>%
  summarise(Count = n())

owt_df01_gb02 <- owt_df01 %>%
  group_by(project) %>%
  summarise(Count = n())

owt_df01_gb03 <- owt_df01 %>%
  group_by(date_sample) %>%
  summarise(Count = n())

owt_df01_gb04 <- owt_df01 %>%
  group_by(date_sample, parameter) %>%
  summarise(Total = mean(value))

print(owt_df01_gb01)
print(owt_df01_gb02)
print(head(owt_df01_gb03))
print(head(owt_df01_gb04))

# Display stations with highest and lowest sample n
print(owt_df01_gb01[owt_df01_gb01$Count == min(owt_df01_gb01$Count), ])
print(owt_df01_gb01[owt_df01_gb01$Count == max(owt_df01_gb01$Count), ])
```

```{r}
print(head(owt_df01_gb04))
param_lst01 <- c("CHLOROPHYLL",
                 "DENSITY", 
                 "DO", 
                 "ENTERO", 
                 "FECAL", 
                 "OG", 
                 "PH", 
                 "SALINITY", 
                 "SUSO", 
                 "TEMP", 
                 "TOTAL", 
                 "XMS")

# Create custom function to cast individual parameters to columns
param_col <- function(param = NA, df = NA) {
  param_df <- df[df$parameter == param, ]
  #print(head(param_df))
  # Citation: https://www.datasciencemadesimple.com/melting-casting-r/
  param_df_cast <- dcast(param_df, date_sample~parameter, mean)
  #print(head(param_df_cast))
  return(param_df_cast)
}

# Run custom function on each of the 12 parameters
owt_df01_gb04_chl <- param_col(param = "CHLOROPHYLL", df = owt_df01_gb04)
#print(owt_df01_gb04_chl)
owt_df01_gb04_den <- param_col(param = "DENSITY", df = owt_df01_gb04)
#print(owt_df01_gb04_den)
owt_df01_gb04_dox <- param_col(param = "DO", df = owt_df01_gb04)
#print(owt_df01_gb04_dox)
owt_df01_gb04_ent <- param_col(param = "ENTERO", df = owt_df01_gb04)
#print(owt_df01_gb04_ent)
owt_df01_gb04_fec <- param_col(param = "FECAL", df = owt_df01_gb04)
#print(owt_df01_gb04_fec)
owt_df01_gb04_org <- param_col(param = "OG", df = owt_df01_gb04)
#print(owt_df01_gb04_org)
owt_df01_gb04_phl <- param_col(param = "PH", df = owt_df01_gb04)
#print(owt_df01_gb04_phl)
owt_df01_gb04_sal <- param_col(param = "SALINITY", df = owt_df01_gb04)
#print(owt_df01_gb04_sal)
owt_df01_gb04_sus <- param_col(param = "SUSO", df = owt_df01_gb04)
#print(owt_df01_gb04_sus)
owt_df01_gb04_tmp <- param_col(param = "TEMP", df = owt_df01_gb04)
#print(owt_df01_gb04_tmp)
owt_df01_gb04_tot <- param_col(param = "TOTAL", df = owt_df01_gb04)
#print(owt_df01_gb04_tot)
owt_df01_gb04_xms <- param_col(param = "XMS", df = owt_df01_gb04)
print("dcasting:")
print(owt_df01_gb04_xms)

# Merge individual casted parameter df's into 1 df
# Citation: https://www.geeksforgeeks.org/joining-of-dataframes-in-r-programming/
owt_df01_gb04_mrgd <- merge(x = owt_df01_gb04_chl,
                            y = owt_df01_gb04_den,
                            by ="date_sample",
                            all = TRUE)

owt_df01_gb04_mrgd <- merge(x = owt_df01_gb04_mrgd,
                            y = owt_df01_gb04_dox,
                            by ="date_sample",
                            all = TRUE)

owt_df01_gb04_mrgd <- merge(x = owt_df01_gb04_mrgd,
                            y = owt_df01_gb04_ent,
                            by ="date_sample",
                            all = TRUE)

owt_df01_gb04_mrgd <- merge(x = owt_df01_gb04_mrgd,
                            y = owt_df01_gb04_fec,
                            by ="date_sample",
                            all = TRUE)

owt_df01_gb04_mrgd <- merge(x = owt_df01_gb04_mrgd,
                            y = owt_df01_gb04_org,
                            by ="date_sample",
                            all = TRUE)

owt_df01_gb04_mrgd <- merge(x = owt_df01_gb04_mrgd,
                            y = owt_df01_gb04_phl,
                            by ="date_sample",
                            all = TRUE)

owt_df01_gb04_mrgd <- merge(x = owt_df01_gb04_mrgd,
                            y = owt_df01_gb04_sal,
                            by ="date_sample",
                            all = TRUE)

owt_df01_gb04_mrgd <- merge(x = owt_df01_gb04_mrgd,
                            y = owt_df01_gb04_sus,
                            by ="date_sample",
                            all = TRUE)

owt_df01_gb04_mrgd <- merge(x = owt_df01_gb04_mrgd,
                            y = owt_df01_gb04_tmp,
                            by ="date_sample",
                            all = TRUE)

owt_df01_gb04_mrgd <- merge(x = owt_df01_gb04_mrgd,
                            y = owt_df01_gb04_tot,
                            by ="date_sample",
                            all = TRUE)

owt_df01_gb04_mrgd <- merge(x = owt_df01_gb04_mrgd,
                            y = owt_df01_gb04_xms,
                            by ="date_sample",
                            all = TRUE)

print(owt_df01_gb04_mrgd)
describe(owt_df01_gb04_mrgd)
```

## Run function to create comparative boxplots
```{r, fig.height=10, fig.width=10}
num_var_lst01 <- c("value")

# Run custom function to ID outliers and generate boxplot
owt_df03 <- subset(x = owt_df01, select = num_var_lst01)
owt_df03 <- na.omit(owt_df03)
print(head(owt_df03))
#box_comp(xcol = num_var_lst01, df = subset(x = owt_df03, select = num_var_lst01), rtn_met = TRUE)
```

```{r, fig.height=10, fig.width=15}

print(head(owt_df01_gb04))
print(tail(owt_df01_gb04))

# Viz time series data for ENTERO parameter
owt_df01_gb04a <- owt_df01_gb04[owt_df01_gb04$parameter == "ENTERO", ]
# & owt_df01_gb04$station == "A1"
aps_df01_ts01 <- ts(owt_df01_gb04a$Total, start = c(1990, 1), freq = 184)
#, start = c(2020, 1), freq = 52
#print(aps_df01_ts01)

#ship_fore_avg <- tslm(aps_df01_ts01 ~ trend)
#ship_fore_trnd <- tslm(aps_df01_ts01 ~ trend + I(trend^2))

plot(aps_df01_ts01,
     xlab = "Time",
     ylab = "Entero Levels",
     type = "o",
     main = "Figure 1. Entero Levels Over Five Years")
grid()

print(acf(aps_df01_ts01, pl=TRUE, na.action = na.pass))
```

