---
title: "Appendix A - ADS506-01-FA22 - Final Project"
author: "Team 1"
date: "12/05/2022"
output:
  pdf_document: default
  html_document:
    df_print: paged
header-includes:
- \usepackage{fvextra}
- \DefineVerbatimEnvironment{Highlighting}{Verbatim}{breaklines,commandchars=\\\{\}}
- \usepackage{pdflscape}
- \newcommand{\blandscape}{\begin{landscape}}
- \newcommand{\elandscape}{\end{landscape}}
---

## RMarkdown global setup
```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

```{r global.options, include=TRUE}
knitr::opts_chunk$set(fig.align = 'center')
```

```{r lib, message=FALSE, warning=FALSE}
library(AppliedPredictiveModeling)
library(BioStatR)
library(car)
library(caret)
library(class)
library(corrplot)
library(datasets)
library(e1071)
library(Hmisc)
library(lubridate)
library(mlbench)
library(gridExtra)
library(psych)
library(randomForest)
library(RANN)
library(reshape2)
library(rpart)
library(rpart.plot)
library(scales)
library(tidyverse)
library(timetk)
library(tsibble)
library(tseries)
library(zoo)

set.seed(1699)
```

## Create custom function to generate boxplots and descriptive statistics for continuous variables
```{r, warning=FALSE}
box_comp <- function(xcol = c(),
                     df = NA,
                     rtn_met = TRUE,
                     grph_title = "All",
                     box = TRUE) {
  # Define function to produce formatted boxplots
  sig <- 3
  metrics_df01 <- data.frame(metric = c("",
                                        "Total N:",
                                        "Count",
                                        "NA Count",
                                        "Mean",
                                        "Median",
                                        "Standard Deviation",
                                        "Variance",
                                        "Range",
                                        "Min",
                                        "Max",
                                        "25th Percentile",
                                        "75th Percentile",
                                        "Subset w/o Outliers:",
                                        "Count",
                                        "%",
                                        "Outlier %",
                                        "NA Count",
                                        "Mean",
                                        "Median",
                                        "Standard Deviation",
                                        "Variance",
                                        "Range",
                                        "Min",
                                        "Max"
                                        ))
  for(var in xcol) {
    df_s1 <- df[, var]
    df_s1s1 <-data.frame(df_s1)
    df_s1_fit <- preProcess(df_s1s1,
                            method = c("center", "scale"))
    df_s1_trans <- predict(df_s1_fit, df_s1s1)

    # Calculate quartiles
    var_iqr_lim <- IQR(df_s1) * 1.5
    var_q1 <- quantile(df_s1, probs = c(.25))
    var_otlow <- var_q1 - var_iqr_lim
    var_q3 <- quantile(df_s1, probs = c(.75))
    var_othigh <- var_q3 + var_iqr_lim
    
    # Subset non-outlier data 
    var_non_otlr_df01 <- subset(df, (abs(df_s1_trans) <= 3))
    #var_non_otlr_df01 <- subset(df, (df_s1 > var_otlow & df_s1 < var_othigh))
    df_s2 <- var_non_otlr_df01[, var]

    # Begin calculating measures of centrality & dispersion
    var_mean <- mean(df_s1, na.remove = TRUE)
    var_non_otlr_df01_trunc_mean <- mean(df_s2, na.remove = TRUE)
    var_med <- median(df_s1)
    var_non_otlr_df01_trunc_med <- median(df_s2)
    var_mode <- mode(df_s1)
    var_non_otlr_df01_trunc_mode <- mode(df_s2)
    var_stde <- sd(df_s1)
    var_non_otlr_df01_trunc_stde <- sd(df_s2)
    var_vari <- var(df_s1)
    var_non_otlr_df01_trunc_vari <- var(df_s2)
    var01_min <- min(df[, var])
    var01_max <- max(df[, var])
    var01_range <- var01_max - var01_min
    var02_min <- min(var_non_otlr_df01[, var])
    var02_max <- max(var_non_otlr_df01[, var])
    var02_range <- var02_max - var02_min
    
    # Configure y-axis min & max to sync graphs
    plot_min <- min(var01_min, var02_min)
    plot_max <- max(var01_max, var02_max)
    nonoutlier_perc <- round((as.numeric(dim(var_non_otlr_df01)[1] / as.numeric(dim(df)[1]))) * 100, 1)
    
    # Fill in metrics table
    measure_val01 <- c(paste0("Variable: ", var),
                       "",
                       as.character(dim(df)[1]),
                       sum(is.na(df_s1)),
                       round(var_mean, sig),
                       round(var_med, sig),
                       round(var_stde, sig),
                       round(var_vari, sig),
                       round(var01_range, sig),
                       round(var01_min, sig),
                       round(var01_max, sig),
                       round(var_q1, sig),
                       round(var_q3, sig),
                       "",
                       as.character(dim(var_non_otlr_df01)[1]),
                       paste0(nonoutlier_perc, "%"),
                       paste0(round(100 - nonoutlier_perc, 1), "%"),
                       sum(is.na(df_s2)),
                       round(var_non_otlr_df01_trunc_mean, sig),
                       round(var_non_otlr_df01_trunc_med, sig),
                       round(var_non_otlr_df01_trunc_stde, sig),
                       round(var_non_otlr_df01_trunc_vari, sig),
                       round(var02_range, sig),
                       round(var02_min, sig),
                       round(var02_max, sig)
                       )
    
    var_name <- paste0("Variable: ", var)
    metrics_df01[, ncol(metrics_df01) + 1] <- measure_val01
}
  # Format boxplot titles based on number of plots
  if(box == TRUE) {
    if(length(xcol == 1)) {
      boxplot(df,
              ylab = "Parameter Values",
              main = paste0("Boxplot for ", xcol, " (", grph_title, ")"))
    }
    else {
      boxplot(df,
              ylab = "Parameter Values",
              main = paste0("Boxplot for Multiple Parameters", " (", grph_title, ")"))
      
    }
  }
  # Return and print metrics table(s)
  if(rtn_met == TRUE) {
    print(metrics_df01)
    return(metrics_df01)
  }
}
```

## Import and merge Datasets
```{r, warning=FALSE}
# Import 4 separate CSV files
setwd('C:/Users/Connie/Documents/Masters Applied Data Science USD/506/Week2/Final Project/Ocean WAter')

#owt_df01a <- read_csv("water_quality_1990_1999_datasd.csv", col_types = cols(date_sample=col_date("%Y-%m-%d")))
#owt_df01b <- read_csv("water_quality_2000_2010_datasd.csv", col_types = cols(date_sample=col_date("%Y-%m-%d")))
#owt_df01c <- read_csv("water_quality_2011_2019_datasd.csv", col_types = cols(date_sample=col_date("%Y-%m-%d")))
#owt_df01d <- read_csv("water_quality_2020_2021_datasd.csv", col_types = cols(date_sample=col_date("%Y-%m-%d")))

owt_df01a <- read.csv("water_quality_1990_1999_datasd.csv", header = TRUE, sep = ",")
owt_df01b <- read.csv("water_quality_2000_2010_datasd.csv", header = TRUE, sep = ",")
owt_df01c <- read.csv("water_quality_2011_2019_datasd.csv", header = TRUE, sep = ",")
owt_df01d <- read.csv("water_quality_2020_2021_datasd.csv", header = TRUE, sep = ",")


# Merge 4 seperate dataframes into 1
owt_df01 <- rbind(owt_df01a, owt_df01b, owt_df01c, owt_df01d)

print(head(owt_df01))
describe(owt_df01)

#write.csv(owt_df01, "C:/Users/acarr/Sync/Programming/Python and R/ADS Markdown Files/ADS-506 Markdown/Final Project/data/Ocean Water/ocean_df01.csv")
```

## Factorize and format column types; print NA counts
```{r}
# List of parameter values
param_lst01 <- c("CHLOROPHYLL",
                 "DENSITY", 
                 "DO", 
                 "ENTERO", 
                 "FECAL", 
                 "OG", 
                 "PH", 
                 "SALINITY", 
                 "SUSO", 
                 "TEMP", 
                 "TOTAL", 
                 "XMS")

# List of col names
col_lst01 <- c("sample",
               "station",
               "date_sample",
               "time",
               "project",
               "parameter",
               "qualifier",
               "units")

# Citation: https://www.geeksforgeeks.org/find-columns-and-rows-with-na-in-r-dataframe/
owt_df02 <- owt_df01
for(c in col_lst01) {
  owt_df02[, c] <- as.factor(owt_df02[, c] )
}

# Generate NA summary tables
# Citation: https://www.geeksforgeeks.org/replace-character-value-with-na-in-r/
owt_df02[owt_df02 == ""] <- NA
print(head(owt_df02))
owt_df02_na <- sapply(owt_df02, function(x) sum(is.na(x)))
owt_df02_notna <- sapply(owt_df02, function(x) sum(!is.na(x)))
owt_df02_tbl01 <- rbind(owt_df02_notna, owt_df02_na)
owt_df02_tbl02 <- rbind(owt_df02_tbl01, round(prop.table(owt_df02_tbl01, margin = 2), 4))
print("All parameters")
print(owt_df02_tbl02)

owt_df02a <- owt_df02[which(is.na(owt_df02), arr.ind=TRUE), ]
#print(head(owt_df02a))

for(p in param_lst01) {
  df = owt_df02[owt_df02$parameter == p, ]
  print(head(df[which(is.na(df$value), arr.ind=TRUE), ]))
  df_na <- sapply(df, function(x) sum(is.na(x)))
  df_notna <- sapply(df, function(x) sum(!is.na(x)))
  df_tbl01 <- rbind(df_notna, df_na)
  df_tbl02 <- rbind(df_tbl01, round(prop.table(df_tbl01, margin = 2), 4))
  rownames(df_tbl02) <- c("Not NA n", "NA n", "Not NA %", "NA %")
  print(p)
  print(df_tbl02) # This table w/ null counts and proportions for each feature not displayed for space purposes
}

# Display value summaries
# Citation: Dave Hurst
params <- owt_df02 %>%
  mutate(unit_def = paste(parameter, qualifier, units)) %>%
  count(unit_def)
print(params)
```

## Bin `depth_m` variable
```{r, warning=FALSE}
owt_df02$date_sample <- as.Date(owt_df02$date_sample, "%Y-%m-%d")

# Create bins for depth_m values
depth_lvls01 <- c("[0,8)",
                  "[8,33)",
                  "[33,47)",
                  "[47,70)",
                  "[70,90)",
                  "[90,112)",
                  "[112,120]",
                  "Unknown")

# Plot distribution of depth_m values
#Citation: https://community.rstudio.com/t/ggplot-x-axis-y-axis-ticks-labels-breaks-and-limits/119123/2
ggplot(owt_df02, aes(x = depth_m)) +
  geom_histogram(color = "black", bins = 40, aes(y = stat(density))) +
  geom_density(col = "blue") +
  labs(title = "Histogram of `depth_m` Feature") +
  scale_x_continuous(breaks=seq(0,120,1)) +
  theme(plot.title = element_text(hjust = 0.5, size = 12))

# Create new column with bins
# Citation: https://www.marsja.se/r-add-column-to-dataframe-based-on-other-columns-conditions-dplyr/
owt_df02 <- mutate(owt_df02, depth_m_bin = case_when(depth_m < 8 ~ "[0,8)",
                                                     depth_m < 33 ~ "[8,33)",
                                                     depth_m < 47 ~ "[33,47)",
                                                     depth_m < 70 ~ "[47,70)",
                                                     depth_m < 90 ~ "[70,90)",
                                                     depth_m < 112 ~ "[90,112)",
                                                     depth_m >= 112 ~ "[112,120]"))

# Replace NAs with "Unknown"
# Citation: https://statisticsglobe.com/r-replace-na-with-0/
owt_df02$depth_m_bin <- replace_na(owt_df02$depth_m_bin, "Unknown")

# Citation: https://www.statology.org/order-bars-ggplot2-bar-chart/
owt_df02$depth_m_bin_factr = factor(owt_df02$depth_m_bin, levels = depth_lvls01)
print(head(owt_df02))

# Display transformed bar chart
ggplot(owt_df02, aes(x = depth_m_bin_factr)) +
  geom_bar() +
  labs(title = "Bar of `depth_m_bin` Feature") +
  theme(plot.title = element_text(hjust = 0.5, size = 12))
```

## Perform several aggregations on the data for performing EDA at multiple levels
```{r}
# Display aggregations by different features
owt_df02_gb01 <- owt_df02 %>%
  group_by(station) %>%
  summarise(Count = n())

print(owt_df02_gb01[owt_df02_gb01$Count == min(owt_df02_gb01$Count), ])
print(owt_df02_gb01[owt_df02_gb01$Count == max(owt_df02_gb01$Count), ])

owt_df02_gb02 <- owt_df02 %>%
  group_by(project) %>%
  summarise(Count = n())

owt_df02_gb03 <- owt_df02 %>%
  group_by(date_sample) %>%
  summarise(Count = n())

# Main DF1
owt_df02_gb04 <- owt_df02 %>%
  group_by(date_sample, parameter) %>%
  summarise(Avg = mean(value, na.remove = TRUE))

owt_df02_gb05 <- owt_df02 %>%
  group_by(parameter) %>%
  summarise(Count = n())

owt_df02_gb06 <- owt_df02 %>%
  group_by(depth_m) %>%
  summarise(Count = n())

# Main DF3
owt_df02_gb07 <- owt_df02 %>%
  group_by(date_sample, project, depth_m_bin, parameter) %>%
  summarise(Avg = mean(value, na.remove = TRUE))

owt_df02_gb08 <- owt_df02 %>%
  group_by(depth_m_bin) %>%
  summarise(Count = n())

# Main DF2
owt_df02_gb09 <- owt_df02 %>%
  group_by(date_sample, project, parameter) %>%
  summarise(Avg = mean(value, na.remove = TRUE))

print(owt_df02_gb01)
print(dim(owt_df02_gb01))
print(owt_df02_gb02)
print(dim(owt_df02_gb02))
print(head(owt_df02_gb03))
print(dim(owt_df02_gb03))
print(head(owt_df02_gb04))
print(dim(owt_df02_gb04))
print(owt_df02_gb05)
print(dim(owt_df02_gb05))
print(owt_df02_gb06)
print(dim(owt_df02_gb06))
print(head(owt_df02_gb07))
print(dim(owt_df02_gb07))
print(owt_df02_gb08)
print(dim(owt_df02_gb08))
print(head(owt_df02_gb09))
print(dim(owt_df02_gb09))
```

## Create custom function to df mutation/casting and boxplot display
```{r, warning=FALSE}
ts_eda <- function(ts_df = NA,
                   form_lead = c(),
                   form_cast = c(),
                   param_lst = c(),
                   l1_col = c(),
                   l1_param = c(),
                   l2_col = c(),
                   l2_param = c(),
                   rtn_met = TRUE,
                   grph_title = "All",
                   box = TRUE,
                   week_agg = FALSE) {
  # Define function to dcast, print boxplot, and print desc stats for each parameter
  dcast_form <- as.formula(paste(paste(form_lead, collapse = "+"), form_cast, sep = "~"))
  print(dcast_form)
  #print(head(ts_df))
  
  counter <- 1
  # Loop to dcast parameters to cols
  for(p in param_lst) {
    sym_param <- sym(p)
    print(sym_param)
    param_df <- ts_df[ts_df[, form_cast] == p, ]
    param_df <- param_df %>%
      drop_na()
    #print(param_df)

    if(week_agg == TRUE) {
      param_df02a <- param_df
      param_df02a$week <- isoweek(param_df02a$date_sample)
      #Citation: https://lubridate.tidyverse.org/reference/round_date.html
      param_df02a$week_end <- ceiling_date(param_df02a$date_sample,
                                           unit = "week",
                                           week_start = getOption("lubridate.week.start", 1))
      #print(head(param_df02a, 10)
      param_df$date_sample <- param_df02a$week_end
    }
        
    # Citation: https://www.datasciencemadesimple.com/melting-casting-r/
    param_df_cast <- dcast(param_df, dcast_form, mean)
    #print(param_df_cast)
    
    if(counter  == 1) {
      ts_df_mrgd <- param_df_cast
    }
    else {
      # Merge individual casted parameter df's into 1 df
      # Citation: https://www.geeksforgeeks.org/joining-of-dataframes-in-r-programming/
      ts_df_mrgd <- merge(x = ts_df_mrgd,
                          y = param_df_cast,
                          by = form_lead,
                          all = TRUE)
    }
    
    # Run custom function to ID outliers and generate boxplot
    #ts_df_mrgd01a <- subset(x = ts_df_mrgd, select = num_var_lst01)
    ts_df_mrgd01a <- na.omit(param_df_cast)
    #print(head(ts_df_mrgd01a))
    dfs1 <- subset(x = ts_df_mrgd01a, select = p)
    dfs1a <- dfs1
    dfs1a$Groups <- grph_title
    box_comp(xcol = p,
             df = dfs1,
             rtn_met = rtn_met,
             box = box)
    #dfs_lst <- list(dfs1)
    #print(dfs_lst)

    #_________________________________________________________________________
    # Create subplots based on additional agg layers
    print(paste0("L2 length = ", length(l2_param)))
    if(length(l2_param) == 0) {
      for(l1 in l1_param) {
        ts_df_mrgd_chl_dmb1 <- ts_df_mrgd01a[(ts_df_mrgd01a[, l1_col] == l1), ]

        # Run custom function to ID outliers and generate boxplot
        #print(head(ts_df_mrgd_chl_dmb1))
        # Citation: https://www.geeksforgeeks.org/handling-errors-in-r-programming/
        dfs2 <- subset(x = ts_df_mrgd_chl_dmb1, select = p)
        dfs2a <- dfs2
        try(dfs2a$Groups <- l1)
        #append(dfs_lst, dfs2)
        try(box_comp(xcol = p,
                     df = dfs2,
                     rtn_met = rtn_met,
                     grph_title = l1,
                     box = box),
            silent = TRUE)
        dfs1a <- rbind(dfs1a, dfs2a)
      }
    }
    else {
      for(l1 in l1_param) {
        for(l2 in l2_param) {
          ts_df_mrgd_chl_dmb1 <- ts_df_mrgd01a[(ts_df_mrgd01a[, l1_col] == l1) & (ts_df_mrgd01a[, l2_col] == l2), ]
  
          # Run custom function to ID outliers and generate boxplot
          #print(head(ts_df_mrgd_chl_dmb1))
          # Citation: https://www.geeksforgeeks.org/handling-errors-in-r-programming/
          dfs3 <- subset(x = ts_df_mrgd_chl_dmb1, select = p)
          dfs3a <- dfs3
          try(dfs3a$Groups <- paste0(l1, ": ", l2))
          #append(dfs_lst, dfs3)
          try(box_comp(xcol = p,
                       df = dfs3,
                       rtn_met = rtn_met,
                       grph_title = paste0(l1, ": ", l2),
                       box = box),
              silent = TRUE)
          dfs1a <- rbind(dfs1a, dfs3a)
        }
      }
    }
    #_________________________________________________________________________
    #print(dim(dfs1a))
    #print(head(dfs1a))
    bx_form <- as.formula(paste(p, "Groups", sep = "~"))
    #print(bx_form)
    boxplot(bx_form,
            dfs1a,
            main = "Boxplot(s)")

    counter <- counter + 1
  }
  print(head(ts_df_mrgd, 10))
  print(describe(ts_df_mrgd))
  
  # Display summary of NA count
  ts_df_na <- sapply(ts_df, function(x) sum(is.na(x)))
  ts_df_notna <- sapply(ts_df, function(x) sum(!is.na(x)))
  ts_df_tbl01 <- rbind(ts_df_notna, ts_df_na)
  ts_df_tbl02 <- rbind(ts_df_tbl01, round(prop.table(ts_df_tbl01, margin = 2), 4))
  rownames(ts_df_tbl02) <- c("Not NA n", "NA n", "Not NA %", "NA %")
  print(ts_df_tbl02) # This table w/ null counts and proportions for each feature not displayed for space purposes
  return(ts_df_mrgd)
}
```

## Run custom function on data aggregated by `date_sample` and `parameter`
```{r}
param_lst02 <- c("CHLOROPHYLL",
                 "DENSITY", 
                 "DO", 
                 "ENTERO", 
                 "FECAL", 
                 "OG", 
                 "PH", 
                 "SALINITY", 
                 "SUSO", 
                 "TEMP", 
                 "XMS")

owt_df02_gb04_mrgd = ts_eda(ts_df = owt_df02_gb04,
                            form_lead = "date_sample",
                            form_cast = "parameter",
                            param_lst = param_lst02,
                            rtn_met = TRUE,
                            box = FALSE
                            )
```

```{r}
owt_df02_gb04_wkly = ts_eda(ts_df = owt_df02_gb04,
                            form_lead = "date_sample",
                            form_cast = "parameter",
                            param_lst = param_lst02,
                            rtn_met = TRUE,
                            box = FALSE,
                            week_agg = TRUE
                            )
```

## Run custom function on data aggregated by `date_sample`, `project` and `parameter`
```{r}
owt_df02_gb09_mrgd = ts_eda(ts_df = owt_df02_gb09,
                            form_lead = c("date_sample", "project"),
                            form_cast = "parameter",
                            param_lst = param_lst02,
                            l1_col = c("project"),
                            l1_param = c("PLOO", "SBOO"),
                            rtn_met = TRUE,
                            box = FALSE,
                            week_agg = FALSE
                            )
```

```{r}
owt_df02_gb09_wkly = ts_eda(ts_df = owt_df02_gb09,
                            form_lead = c("date_sample", "project"),
                            form_cast = "parameter",
                            param_lst = param_lst02,
                            l1_col = c("project"),
                            l1_param = c("PLOO", "SBOO"),
                            rtn_met = TRUE,
                            box = FALSE,
                            week_agg = TRUE
                            )
```

## Run custom function on data aggregated by `date_sample`, `project`, `depth_m_bin` and `parameter`
```{r warning=FALSE}
#, fig.height=10, fig.width=25
owt_df02_gb07_mrgd = ts_eda(ts_df = owt_df02_gb07,
                            form_lead = c("date_sample", "project", "depth_m_bin"),
                            form_cast = "parameter",
                            param_lst = param_lst02,
                            l1_col = c("project"),
                            l1_param = c("PLOO", "SBOO"),
                            l2_col = c("depth_m_bin"),
                            l2_param = depth_lvls01,
                            rtn_met = FALSE,
                            box = FALSE
                            )
```

```{r}
owt_df02_gb07_wkly = ts_eda(ts_df = owt_df02_gb07,
                            form_lead = c("date_sample", "project", "depth_m_bin"),
                            form_cast = "parameter",
                            param_lst = param_lst02,
                            l1_col = c("project"),
                            l1_param = c("PLOO", "SBOO"),
                            l2_col = c("depth_m_bin"),
                            l2_param = depth_lvls01,
                            rtn_met = FALSE,
                            box = FALSE,
                            week_agg = TRUE
                            )
```

```{r EDA-CC-linearinterpolation}

# http://publish.illinois.edu/spencer-guerrero/2014/12/11/2-dealing-with-missing-data-in-r-omit-approx-or-spline-part-1/


library(imputeTS)


# Define function that imputes the missing values to parameter dataframe using linear interpolation
impute_missing_values <- function(df_data) {
  
    params <- c("CHLOROPHYLL", "DENSITY", "DO", "ENTERO", "FECAL", "OG", "PH", "SALINITY", "SUSO", "TEMP", "XMS")
  
  for (param in params) {
    print(head(df_data))
    print(param)
    print(date_sample)
    
    x <- zoo(df_data$param, df_data$date_sample)
    df_data$param <- na.interpolation(x, option = "linear")
    return(df_data)
  
  }
}

# remove NAs using Linear Interpolation  na.interpolation()
library(imputeTS)

# Merged Table
copy_owt_df02_gb04_mrgd <- data.frame(owt_df02_gb04_mrgd)

x <- zoo(copy_owt_df02_gb04_mrgd$CHLOROPHYLL, copy_owt_df02_gb04_mrgd$date_sample)
copy_owt_df02_gb04_mrgd$CHLOROPHYLL <- na.interpolation(x, option = "linear")

x <- zoo(copy_owt_df02_gb04_mrgd$DENSITY, copy_owt_df02_gb04_mrgd$date_sample)
copy_owt_df02_gb04_mrgd$DENSITY <- na.interpolation(x, option = "linear")

x <- zoo(copy_owt_df02_gb04_mrgd$DO, copy_owt_df02_gb04_mrgd$date_sample)
copy_owt_df02_gb04_mrgd$DO <- na.interpolation(x, option = "linear")

x <- zoo(copy_owt_df02_gb04_mrgd$ENTERO, copy_owt_df02_gb04_mrgd$date_sample)
copy_owt_df02_gb04_mrgd$ENTERO <- na.interpolation(x, option = "linear")

x <- zoo(copy_owt_df02_gb04_mrgd$FECAL, copy_owt_df02_gb04_mrgd$date_sample)
copy_owt_df02_gb04_mrgd$FECAL <- na.interpolation(x, option = "linear")

x <- zoo(copy_owt_df02_gb04_mrgd$OG, copy_owt_df02_gb04_mrgd$date_sample)
copy_owt_df02_gb04_mrgd$OG <- na.interpolation(x, option = "linear")

x <- zoo(copy_owt_df02_gb04_mrgd$PH, copy_owt_df02_gb04_mrgd$date_sample)
copy_owt_df02_gb04_mrgd$PH <- na.interpolation(x, option = "linear")

x <- zoo(copy_owt_df02_gb04_mrgd$SALINITY, copy_owt_df02_gb04_mrgd$date_sample)
copy_owt_df02_gb04_mrgd$SALINITY <- na.interpolation(x, option = "linear")

x <- zoo(copy_owt_df02_gb04_mrgd$SUSO, copy_owt_df02_gb04_mrgd$date_sample)
copy_owt_df02_gb04_mrgd$SUSO <- na.interpolation(x, option = "linear")

x <- zoo(copy_owt_df02_gb04_mrgd$TEMP, copy_owt_df02_gb04_mrgd$date_sample)
copy_owt_df02_gb04_mrgd$TEMP <- na.interpolation(x, option = "linear")

x <- zoo(copy_owt_df02_gb04_mrgd$XMS, copy_owt_df02_gb04_mrgd$date_sample)
copy_owt_df02_gb04_mrgd$XMS <- na.interpolation(x, option = "linear")

# plot without interpolation and with interpolation
# only plot a year (1996) so that it's easier to see
df_original <- subset(owt_df02_gb04_mrgd, format(as.Date(date_sample),"%Y")==1996,)
copy_owt_df02_gb04_mrgd <- subset(owt_df02_gb04_mrgd, format(as.Date(date_sample),"%Y")==1996,)

print(ggplot(df_original, aes(x = date_sample, y = CHLOROPHYLL)) +
       geom_line() +
       theme(axis.text.x = element_text(angle = 45, hjust = 1))+
       scale_x_date(date_labels = "%Y-%b", breaks = date_breaks("1 month")) +ggtitle(paste0("df02_gb04_mrgd - ", "original")))

print(ggplot(copy_owt_df02_gb04_mrgd, aes(x = date_sample, y = CHLOROPHYLL)) +
       geom_line() +
       theme(axis.text.x = element_text(angle = 45, hjust = 1))+
       scale_x_date(date_labels = "%Y-%b", breaks = date_breaks("1 month")) +ggtitle(paste0("df02_gb04_mrgd - ", "na.interpolation")))

# TEMP
print(ggplot(df_original, aes(x = date_sample, y = TEMP)) +
       geom_line() +
       theme(axis.text.x = element_text(angle = 45, hjust = 1))+
       scale_x_date(date_labels = "%Y-%b", breaks = date_breaks("1 month")) +ggtitle(paste0("df02_gb04_mrgd - TEMP - ", "original")))

print(ggplot(copy_owt_df02_gb04_mrgd, aes(x = date_sample, y = TEMP)) +
       geom_line() +
       theme(axis.text.x = element_text(angle = 45, hjust = 1))+
       scale_x_date(date_labels = "%Y-%b", breaks = date_breaks("1 month")) +ggtitle(paste0("df02_gb04_mrgd - TEMP - ", "na.interpolation")))

# XMS
print(ggplot(df_original, aes(x = date_sample, y = XMS)) +
       geom_line() +
       theme(axis.text.x = element_text(angle = 45, hjust = 1))+
       scale_x_date(date_labels = "%Y-%b", breaks = date_breaks("1 month")) +ggtitle(paste0("df02_gb04_mrgd - XMS - ", "original")))

print(ggplot(copy_owt_df02_gb04_mrgd, aes(x = date_sample, y = XMS)) +
       geom_line() +
       theme(axis.text.x = element_text(angle = 45, hjust = 1))+
       scale_x_date(date_labels = "%Y-%b", breaks = date_breaks("1 month")) +ggtitle(paste0("df02_gb04_mrgd - XMS - ", "na.interpolation")))


# SUSO
print(ggplot(df_original, aes(x = date_sample, y = SUSO)) +
       geom_line() +
       theme(axis.text.x = element_text(angle = 45, hjust = 1))+
       scale_x_date(date_labels = "%Y-%b", breaks = date_breaks("1 month")) +ggtitle(paste0("df02_gb04_mrgd - SUSO - ", "original")))

print(ggplot(copy_owt_df02_gb04_mrgd, aes(x = date_sample, y = SUSO)) +
       geom_line() +
       theme(axis.text.x = element_text(angle = 45, hjust = 1))+
       scale_x_date(date_labels = "%Y-%b", breaks = date_breaks("1 month")) +ggtitle(paste0("df02_gb04_mrgd - SUSO - ", "na.interpolation")))

# DO
print(ggplot(df_original, aes(x = date_sample, y = DO)) +
       geom_line() +
       theme(axis.text.x = element_text(angle = 45, hjust = 1))+
       scale_x_date(date_labels = "%Y-%b", breaks = date_breaks("1 month")) +ggtitle(paste0("df02_gb04_mrgd - DO - ", "original")))

print(ggplot(copy_owt_df02_gb04_mrgd, aes(x = date_sample, y = DO)) +
       geom_line() +
       theme(axis.text.x = element_text(angle = 45, hjust = 1))+
       scale_x_date(date_labels = "%Y-%b", breaks = date_breaks("1 month")) +ggtitle(paste0("df02_gb04_mrgd - DO - ", "na.interpolation")))


# ENTERO
print(ggplot(df_original, aes(x = date_sample, y = ENTERO)) +
       geom_line() +
       theme(axis.text.x = element_text(angle = 45, hjust = 1))+
       scale_x_date(date_labels = "%Y-%b", breaks = date_breaks("1 month")) +ggtitle(paste0("df02_gb04_mrgd - ENTERO - ", "original")))

print(ggplot(copy_owt_df02_gb04_mrgd, aes(x = date_sample, y = ENTERO)) +
       geom_line() +
       theme(axis.text.x = element_text(angle = 45, hjust = 1))+
       scale_x_date(date_labels = "%Y-%b", breaks = date_breaks("1 month")) +ggtitle(paste0("df02_gb04_mrgd - ENTERO - ", "na.interpolation")))


# PH
print(ggplot(df_original, aes(x = date_sample, y = PH)) +
       geom_line() +
       theme(axis.text.x = element_text(angle = 45, hjust = 1))+
       scale_x_date(date_labels = "%Y-%b", breaks = date_breaks("1 month")) +ggtitle(paste0("df02_gb04_mrgd - PH - ", "original")))

print(ggplot(copy_owt_df02_gb04_mrgd, aes(x = date_sample, y = PH)) +
       geom_line() +
       theme(axis.text.x = element_text(angle = 45, hjust = 1))+
       scale_x_date(date_labels = "%Y-%b", breaks = date_breaks("1 month")) +ggtitle(paste0("df02_gb04_mrgd - PH - ", "na.interpolation")))

# OG
print(ggplot(df_original, aes(x = date_sample, y = OG)) +
       geom_line() +
       theme(axis.text.x = element_text(angle = 45, hjust = 1))+
       scale_x_date(date_labels = "%Y-%b", breaks = date_breaks("1 month")) +ggtitle(paste0("df02_gb04_mrgd - OG - ", "original")))

print(ggplot(copy_owt_df02_gb04_mrgd, aes(x = date_sample, y = OG)) +
       geom_line() +
       theme(axis.text.x = element_text(angle = 45, hjust = 1))+
       scale_x_date(date_labels = "%Y-%b", breaks = date_breaks("1 month")) +ggtitle(paste0("df02_gb04_mrgd - OG - ", "na.interpolation")))

###############
copy_owt_df02_gb04_wkly <- data.frame(owt_df02_gb04_wkly)

# copy_owt_df02_gb04_wkly
x <- zoo(copy_owt_df02_gb04_wkly$CHLOROPHYLL, copy_owt_df02_gb04_wkly$date_sample)
copy_owt_df02_gb04_wkly$CHLOROPHYLL <- na.interpolation(x, option = "linear")

x <- zoo(copy_owt_df02_gb04_wkly$DENSITY, copy_owt_df02_gb04_wkly$date_sample)
copy_owt_df02_gb04_wkly$DENSITY <- na.interpolation(x, option = "linear")

x <- zoo(copy_owt_df02_gb04_wkly$DO, copy_owt_df02_gb04_wkly$date_sample)
copy_owt_df02_gb04_wkly$DO <- na.interpolation(x, option = "linear")

x <- zoo(copy_owt_df02_gb04_wkly$ENTERO, copy_owt_df02_gb04_wkly$date_sample)
copy_owt_df02_gb04_wkly$ENTERO <- na.interpolation(x, option = "linear")

x <- zoo(copy_owt_df02_gb04_wkly$FECAL, copy_owt_df02_gb04_wkly$date_sample)
copy_owt_df02_gb04_wkly$FECAL <- na.interpolation(x, option = "linear")

x <- zoo(copy_owt_df02_gb04_wkly$OG, copy_owt_df02_gb04_wkly$date_sample)
copy_owt_df02_gb04_wkly$OG <- na.interpolation(x, option = "linear")

x <- zoo(copy_owt_df02_gb04_wkly$PH, copy_owt_df02_gb04_wkly$date_sample)
copy_owt_df02_gb04_wkly$PH <- na.interpolation(x, option = "linear")

x <- zoo(copy_owt_df02_gb04_wkly$SALINITY, copy_owt_df02_gb04_wkly$date_sample)
copy_owt_df02_gb04_wkly$SALINITY <- na.interpolation(x, option = "linear")

x <- zoo(copy_owt_df02_gb04_wkly$SUSO, copy_owt_df02_gb04_wkly$date_sample)
copy_owt_df02_gb04_wkly$SUSO <- na.interpolation(x, option = "linear")

x <- zoo(copy_owt_df02_gb04_wkly$TEMP, copy_owt_df02_gb04_wkly$date_sample)
copy_owt_df02_gb04_wkly$TEMP <- na.interpolation(x, option = "linear")

x <- zoo(copy_owt_df02_gb04_wkly$XMS, copy_owt_df02_gb04_wkly$date_sample)
copy_owt_df02_gb04_wkly$XMS <- na.interpolation(x, option = "linear")


###############
copy_owt_df02_gb09_mrgd <- data.frame(owt_df02_gb09_mrgd)
# copy_owt_df02_gb09_mrgd
x <- zoo(copy_owt_df02_gb09_mrgd$CHLOROPHYLL, copy_owt_df02_gb09_mrgd$date_sample)
copy_owt_df02_gb09_mrgd$CHLOROPHYLL <- na.interpolation(x, option = "linear")

x <- zoo(copy_owt_df02_gb09_mrgd$DENSITY, copy_owt_df02_gb09_mrgd$date_sample)
copy_owt_df02_gb09_mrgd$DENSITY <- na.interpolation(x, option = "linear")


x <- zoo(copy_owt_df02_gb09_mrgd$DO, copy_owt_df02_gb09_mrgd$date_sample)
copy_owt_df02_gb09_mrgd$DO <- na.interpolation(x, option = "linear")

x <- zoo(copy_owt_df02_gb09_mrgd$ENTERO, copy_owt_df02_gb09_mrgd$date_sample)
copy_owt_df02_gb09_mrgd$ENTERO <- na.interpolation(x, option = "linear")

x <- zoo(copy_owt_df02_gb09_mrgd$FECAL, copy_owt_df02_gb09_mrgd$date_sample)
copy_owt_df02_gb09_mrgd$FECAL <- na.interpolation(x, option = "linear")

x <- zoo(copy_owt_df02_gb09_mrgd$OG, copy_owt_df02_gb09_mrgd$date_sample)
copy_owt_df02_gb09_mrgd$OG <- na.interpolation(x, option = "linear")

x <- zoo(copy_owt_df02_gb09_mrgd$PH, copy_owt_df02_gb09_mrgd$date_sample)
copy_owt_df02_gb09_mrgd$PH <- na.interpolation(x, option = "linear")

x <- zoo(copy_owt_df02_gb09_mrgd$SALINITY, copy_owt_df02_gb09_mrgd$date_sample)
copy_owt_df02_gb09_mrgd$SALINITY <- na.interpolation(x, option = "linear")

x <- zoo(copy_owt_df02_gb09_mrgd$SUSO, copy_owt_df02_gb09_mrgd$date_sample)
copy_owt_df02_gb09_mrgd$SUSO <- na.interpolation(x, option = "linear")

x <- zoo(copy_owt_df02_gb09_mrgd$TEMP, copy_owt_df02_gb09_mrgd$date_sample)
copy_owt_df02_gb09_mrgd$TEMP <- na.interpolation(x, option = "linear")

x <- zoo(copy_owt_df02_gb09_mrgd$XMS, copy_owt_df02_gb09_mrgd$date_sample)
copy_owt_df02_gb09_mrgd$XMS <- na.interpolation(x, option = "linear")



###############
copy_owt_df02_gb09_wkly <- data.frame(owt_df02_gb09_wkly)
x <- zoo(copy_owt_df02_gb09_wkly$CHLOROPHYLL, copy_owt_df02_gb09_wkly$date_sample)
copy_owt_df02_gb09_wkly$CHLOROPHYLL <- na.interpolation(x, option = "linear")

x <- zoo(copy_owt_df02_gb09_wkly$DENSITY, copy_owt_df02_gb09_wkly$date_sample)
copy_owt_df02_gb09_wkly$DENSITY <- na.interpolation(x, option = "linear")

x <- zoo(copy_owt_df02_gb09_wkly$DO, copy_owt_df02_gb09_wkly$date_sample)
copy_owt_df02_gb09_wkly$DO <- na.interpolation(x, option = "linear")

x <- zoo(copy_owt_df02_gb09_wkly$ENTERO, copy_owt_df02_gb09_wkly$date_sample)
copy_owt_df02_gb09_wkly$ENTERO <- na.interpolation(x, option = "linear")

x <- zoo(copy_owt_df02_gb09_wkly$FECAL, copy_owt_df02_gb09_wkly$date_sample)
copy_owt_df02_gb09_wkly$FECAL <- na.interpolation(x, option = "linear")

x <- zoo(copy_owt_df02_gb09_wkly$OG, copy_owt_df02_gb09_wkly$date_sample)
copy_owt_df02_gb09_wkly$OG <- na.interpolation(x, option = "linear")

x <- zoo(copy_owt_df02_gb09_wkly$PH, copy_owt_df02_gb09_wkly$date_sample)
copy_owt_df02_gb09_wkly$PH <- na.interpolation(x, option = "linear")

x <- zoo(copy_owt_df02_gb09_wkly$SALINITY, copy_owt_df02_gb09_wkly$date_sample)
copy_owt_df02_gb09_wkly$SALINITY <- na.interpolation(x, option = "linear")

x <- zoo(copy_owt_df02_gb09_wkly$SUSO, copy_owt_df02_gb09_wkly$date_sample)
copy_owt_df02_gb09_wkly$SUSO <- na.interpolation(x, option = "linear")

x <- zoo(copy_owt_df02_gb09_wkly$TEMP, copy_owt_df02_gb09_wkly$date_sample)
copy_owt_df02_gb09_wkly$TEMP <- na.interpolation(x, option = "linear")

x <- zoo(copy_owt_df02_gb09_wkly$XMS, copy_owt_df02_gb09_wkly$date_sample)
copy_owt_df02_gb09_wkly$XMS <- na.interpolation(x, option = "linear")


###############
copy_owt_df02_gb07_mrgd <- data.frame(owt_df02_gb07_mrgd)

x <- zoo(copy_owt_df02_gb07_mrgd$CHLOROPHYLL, copy_owt_df02_gb07_mrgd$date_sample)
copy_owt_df02_gb07_mrgd$CHLOROPHYLL <- na.interpolation(x, option = "linear")

x <- zoo(copy_owt_df02_gb07_mrgd$DENSITY, copy_owt_df02_gb07_mrgd$date_sample)
copy_owt_df02_gb07_mrgd$DENSITY <- na.interpolation(x, option = "linear")

x <- zoo(copy_owt_df02_gb07_mrgd$DO, copy_owt_df02_gb07_mrgd$date_sample)
copy_owt_df02_gb07_mrgd$DO <- na.interpolation(x, option = "linear")

x <- zoo(copy_owt_df02_gb07_mrgd$ENTERO, copy_owt_df02_gb07_mrgd$date_sample)
copy_owt_df02_gb07_mrgd$ENTERO <- na.interpolation(x, option = "linear")

x <- zoo(copy_owt_df02_gb07_mrgd$FECAL, copy_owt_df02_gb07_mrgd$date_sample)
copy_owt_df02_gb07_mrgd$FECAL <- na.interpolation(x, option = "linear")

x <- zoo(copy_owt_df02_gb07_mrgd$OG, copy_owt_df02_gb07_mrgd$date_sample)
copy_owt_df02_gb07_mrgd$OG <- na.interpolation(x, option = "linear")

x <- zoo(copy_owt_df02_gb07_mrgd$PH, copy_owt_df02_gb07_mrgd$date_sample)
copy_owt_df02_gb07_mrgd$PH <- na.interpolation(x, option = "linear")

x <- zoo(copy_owt_df02_gb07_mrgd$SALINITY, copy_owt_df02_gb07_mrgd$date_sample)
copy_owt_df02_gb07_mrgd$SALINITY <- na.interpolation(x, option = "linear")

x <- zoo(copy_owt_df02_gb07_mrgd$SUSO, copy_owt_df02_gb07_mrgd$date_sample)
copy_owt_df02_gb07_mrgd$SUSO <- na.interpolation(x, option = "linear")

x <- zoo(copy_owt_df02_gb07_mrgd$TEMP, copy_owt_df02_gb07_mrgd$date_sample)
copy_owt_df02_gb07_mrgd$TEMP <- na.interpolation(x, option = "linear")

x <- zoo(copy_owt_df02_gb07_mrgd$XMS, copy_owt_df02_gb07_mrgd$date_sample)
copy_owt_df02_gb07_mrgd$XMS <- na.interpolation(x, option = "linear")


###############
copy_owt_df02_gb07_wkly <- data.frame(owt_df02_gb07_wkly)

x <- zoo(copy_owt_df02_gb07_wkly$CHLOROPHYLL, copy_owt_df02_gb07_wkly$date_sample)
copy_owt_df02_gb07_wkly$CHLOROPHYLL <- na.interpolation(x, option = "linear")

x <- zoo(copy_owt_df02_gb07_wkly$DENSITY, copy_owt_df02_gb07_wkly$date_sample)
copy_owt_df02_gb07_wkly$DENSITY <- na.interpolation(x, option = "linear")

x <- zoo(copy_owt_df02_gb07_wkly$DO, copy_owt_df02_gb07_wkly$date_sample)
copy_owt_df02_gb07_wkly$DO <- na.interpolation(x, option = "linear")

x <- zoo(copy_owt_df02_gb07_wkly$ENTERO, copy_owt_df02_gb07_wkly$date_sample)
copy_owt_df02_gb07_wkly$ENTERO <- na.interpolation(x, option = "linear")

x <- zoo(copy_owt_df02_gb07_wkly$FECAL, copy_owt_df02_gb07_wkly$date_sample)
copy_owt_df02_gb07_wkly$FECAL <- na.interpolation(x, option = "linear")

x <- zoo(copy_owt_df02_gb07_wkly$OG, copy_owt_df02_gb07_wkly$date_sample)
copy_owt_df02_gb07_wkly$OG <- na.interpolation(x, option = "linear")

x <- zoo(copy_owt_df02_gb07_wkly$PH, copy_owt_df02_gb07_wkly$date_sample)
copy_owt_df02_gb07_wkly$PH <- na.interpolation(x, option = "linear")

x <- zoo(copy_owt_df02_gb07_wkly$SALINITY, copy_owt_df02_gb07_wkly$date_sample)
copy_owt_df02_gb07_wkly$SALINITY <- na.interpolation(x, option = "linear")

x <- zoo(copy_owt_df02_gb07_wkly$SUSO, copy_owt_df02_gb07_wkly$date_sample)
copy_owt_df02_gb07_wkly$SUSO <- na.interpolation(x, option = "linear")

x <- zoo(copy_owt_df02_gb07_wkly$TEMP, copy_owt_df02_gb07_wkly$date_sample)
copy_owt_df02_gb07_wkly$TEMP <- na.interpolation(x, option = "linear")

x <- zoo(copy_owt_df02_gb07_wkly$XMS, copy_owt_df02_gb07_wkly$date_sample)
copy_owt_df02_gb07_wkly$XMS <- na.interpolation(x, option = "linear")






```
```{r CC-EDA-PAD-MISSINGDATES}

# https://cran.r-project.org/web/packages/padr/vignettes/padr.html
library(padr)
library(dplyr)

copy_owt_df02_gb04_mrgd %>% pad()

####### 5 YEAR - 1996 - 2001 #######################################
ts_chlorophyll <- ts(copy_owt_df02_gb04_mrgd$CHLOROPHYLL, start = c(1996, 1), freq = 365)
ts_1996_2001_chl <- window(ts_chlorophyll, start=c(1996, 1), end=c(2001, 1))
stl_chl <- stl(ts_1996_2001_chl, s.window="periodic")
#labels.chart = seq(as.Date("1990-11-15"), as.Date("2021-12-29"), by = "weeks")
plot(stl_chl)
mtext("CHLOROPHYLL", side=3, line = -5)


ts_do <- ts(copy_owt_df02_gb04_mrgd$DO, start = c(1996, 1), freq = 365)
ts_1996_2001_do <- window(ts_do, start=c(1996, 1), end=c(2001, 1))
stl_do <- stl(ts_1996_2001_do, s.window="periodic")
#labels.chart = seq(as.Date("1990-11-15"), as.Date("2021-12-29"), by = "weeks")
plot(stl_do)
mtext("DO", side=3, line = -5)


ts_ent <- ts(copy_owt_df02_gb04_mrgd$ENTERO, start = c(1996, 1), freq = 365)
ts_1996_2001_ent <- window(ts_ent, start=c(1996, 1), end=c(2001, 1))
stl_ent <- stl(ts_1996_2001_ent, s.window="periodic")
#labels.chart = seq(as.Date("1990-11-15"), as.Date("2021-12-29"), by = "weeks")
plot(stl_ent)
mtext("ENTERO", side=3, line = -5)


ts_fecal <- ts(copy_owt_df02_gb04_mrgd$FECAL, start = c(1996, 1), freq = 365)
ts_1996_2001_fecal <- window(ts_fecal, start=c(1996, 1), end=c(2001, 1))
stl_fecal <- stl(ts_1996_2001_fecal, s.window="periodic")
#labels.chart = seq(as.Date("1990-11-15"), as.Date("2021-12-29"), by = "weeks")
plot(stl_fecal)
mtext("FECAL", side=3, line = -5)


ts_og <- ts(copy_owt_df02_gb04_mrgd$OG, start = c(1996, 1), freq = 365)
ts_1996_2001_og <- window(ts_og, start=c(1996, 1), end=c(2001, 1))
stl_og <- stl(ts_1996_2001_og, s.window="periodic")
#labels.chart = seq(as.Date("1990-11-15"), as.Date("2021-12-29"), by = "weeks")
plot(stl_og)
mtext("OG", side=3, line = -5)


ts_ph <- ts(copy_owt_df02_gb04_mrgd$PH, start = c(1996, 1), freq = 365)
ts_1996_2001_ph <- window(ts_ph, start=c(1996, 1), end=c(2001, 1))
stl_ph <- stl(ts_1996_2001_ph, s.window="periodic")
#labels.chart = seq(as.Date("1990-11-15"), as.Date("2021-12-29"), by = "weeks")
plot(stl_ph)
mtext("PH", side=3, line = -5)


ts_salinity <- ts(copy_owt_df02_gb04_mrgd$SALINITY, start = c(1996, 1), freq = 365)
ts_1996_2001_salinity <- window(ts_salinity, start=c(1996, 1), end=c(2001, 1))
stl_salinity <- stl(ts_1996_2001_salinity, s.window="periodic")
#labels.chart = seq(as.Date("1990-11-15"), as.Date("2021-12-29"), by = "weeks")
plot(stl_salinity)
mtext("SALINITY", side=3, line = -5)


ts_suso <- ts(copy_owt_df02_gb04_mrgd$SUSO, start = c(1996, 1), freq = 365)
ts_1996_2001_suso <- window(ts_suso, start=c(1996, 1), end=c(2001, 1))
stl_suso <- stl(ts_1996_2001_suso, s.window="periodic")
#labels.chart = seq(as.Date("1990-11-15"), as.Date("2021-12-29"), by = "weeks")
plot(stl_suso)
mtext("SUSO", side=3, line = -5)


ts_temp <- ts(copy_owt_df02_gb04_mrgd$TEMP, start = c(1996, 1), freq = 365)
ts_1996_2001_temp <- window(ts_temp, start=c(1996, 1), end=c(2001, 1))
stl_temp <- stl(ts_1996_2001_temp, s.window="periodic")
#labels.chart = seq(as.Date("1990-11-15"), as.Date("2021-12-29"), by = "weeks")
plot(stl_temp)
mtext("TEMP", side=3, line = -5)


ts_xms <- ts(copy_owt_df02_gb04_mrgd$XMS, start = c(1996, 1), freq = 365)
ts_1996_2001_xms <- window(ts_xms, start=c(1996, 1), end=c(2001, 1))
stl_xms <- stl(ts_1996_2001_xms, s.window="periodic")
#labels.chart = seq(as.Date("1990-11-15"), as.Date("2021-12-29"), by = "weeks")
plot(stl_xms)
mtext("XMS", side=3, line = -5)


```


```{r CC-EDA-STL-1YEARPERIOD}

#https://cran.r-project.org/web/packages/stR/vignettes/stRvignette.html

####### 1 YEAR - 2001 #######################################
ts_chlorophyll <- ts(copy_owt_df02_gb04_mrgd$CHLOROPHYLL, start = c(2001, 1), freq = 365)
ts_1996_2001_chl <- window(ts_chlorophyll, start=c(2001, 1), end=c(2001, 2))
plot(ts_1996_2001_chl)
stl_chl <- stl(ts_1996_2001_chl, s.window="periodic")
#labels.chart = seq(as.Date("1990-11-15"), as.Date("2021-12-29"), by = "weeks")
plot(stl_chl)
mtext("CHLOROPHYLL", side=3, line = -5)

```

```{r CC-PREPROCESING-TRAINSPLIT}

library(forecast)

# All parameters exhibited seasonal cycles within a year range, so
# it would make sense to have several years worth of datapoints for the training period.  This set below can be used for all parameters.
train <- head(copy_owt_df02_gb04_mrgd, round(NROW(copy_owt_df02_gb04_mrgd) * 0.6))
h <- length(copy_owt_df02_gb04_mrgd) - NROW(train)
test <- tail(copy_owt_df02_gb04_mrgd, h)

```


## Display new dataframes
```{r}
#print(head(owt_df02_gb04_mrgd, 10))
#print(head(owt_df02_gb09_mrgd, 10))
#print(head(owt_df02_gb07_mrgd, 10))

owt_df02_gb04_tbbl <- as_tibble(owt_df02_gb04_mrgd, index = date_sample)
owt_df02_gb04_wkly_tbbl <- as_tibble(owt_df02_gb04_wkly, index = date_sample)
owt_df02_gb09_tbbl <- as_tibble(owt_df02_gb09_mrgd, key = project, index = date_sample)
owt_df02_gb09_wkly_tbbl <- as_tibble(owt_df02_gb09_wkly, key = project, index = date_sample)
owt_df02_gb07_tbbl <- as_tibble(owt_df02_gb07_mrgd, key = c(project, depth_m_bin), index = date_sample)
owt_df02_gb07_wkly_tbbl <- as_tibble(owt_df02_gb07_wkly, key = c(project, depth_m_bin), index = date_sample)

print(head(owt_df02_gb04_tbbl, 10))
print(head(owt_df02_gb04_wkly_tbbl, 10))
print(head(owt_df02_gb09_tbbl, 10))
print(head(owt_df02_gb09_wkly_tbbl, 10))
print(head(owt_df02_gb07_tbbl, 10))
print(head(owt_df02_gb07_wkly_tbbl, 10))
```

## Convert dataframes to tsibbles
{r}
#_________________________________________________________________________
owt_df02_gb04_tbbl01 <- owt_df02_gb04_mrgd[c("date_sample", "CHLOROPHYLL")] %>%
  drop_na() %>%
  group_by(date_sample) %>%
  summarise_by_time(.date_var = date_sample,
                    .by = "week",
                    .week_start = 1,
                    CHLOROPHYLL = mean(CHLOROPHYLL, na.remove = TRUE)
                    )

print(head(owt_df02_gb04_tbbl01, 10))
print(duplicates(owt_df02_gb04_tbbl01, index = date_sample))

#_________________________________________________________________________
owt_df02_gb04_tbbl02 <- owt_df02_gb04_mrgd[c("date_sample", "ENTERO")] %>%
  drop_na() %>%
  group_by(date_sample) %>%
  summarise_by_time(.date_var = date_sample,
                    .by = "week",
                    .week_start = 1,
                    ENTERO = mean(ENTERO, na.remove = TRUE)
                    )

print(head(owt_df02_gb04_tbbl02, 10))
print(duplicates(owt_df02_gb04_tbbl02, index = date_sample))

owt_df02_gb04_tbb_mrgd <- merge(x = owt_df02_gb04_tbbl01,
                    y = owt_df02_gb04_tbbl02,
                    by = "date_sample",
                    all = TRUE)
print(head(owt_df02_gb04_tbb_mrgd, 10))



{r}
owt_df02_gb09_tbbl01a <- owt_df02_gb09_tbbl01[1:3]
print(head(owt_df02_gb09_tbbl01a))
owt_df02_gb09_tbbl01a %>%
  group_by_key() %>%
  index_by(year_week = ~ yearweek(date_sample)) %>% # monthly aggregates
  summarise(CHLOROPHYLL_avg = mean(CHLOROPHYLL, na.rm = TRUE))

#print(head(owt_df02_gb09_tbbl02, 100))


## Plot time series for selected parameters and tsibbles
```{r}
#, fig.height=10, fig.width=15
#print(head(owt_df02_gb04_tbbl01$CHLOROPHYLL))
#print(tail(owt_df02_gb04_tbbl01$CHLOROPHYLL))

# Viz time series data for ENTERO parameter
#owt_df02_gb04a <- owt_df02_gb04[owt_df02_gb04$parameter == "ENTERO", ]
# & owt_df02_gb04$station == "A1"
#aps_df01_ts01 <- ts(owt_df02_gb04a$Avg, start = c(1990, 1), freq = 184)
#, start = c(2020, 1), freq = 52
#print(aps_df01_ts01)

#ship_fore_avg <- tslm(aps_df01_ts01 ~ trend)
#ship_fore_trnd <- tslm(aps_df01_ts01 ~ trend + I(trend^2))

#plot(owt_df02_gb04_mrgd$ENTERO,
#     xlab = "Time",
#     ylab = "ENTERO Levels",
#     type = "o",
#     main = "ENTERO Levels Over Time")
#grid()
print(acf(owt_df02_gb04_wkly$ENTERO, pl=TRUE, na.action = na.pass))
# Citation: https://www.geeksforgeeks.org/time-series-visualization-with-ggplot2-in-r/
ggplot(owt_df02_gb04_wkly, aes(x=date_sample, y=ENTERO, group = 1)) +
  geom_line()

owt_df02_gb09_wkly01a <- owt_df02_gb09_wkly[owt_df02_gb09_wkly$project == "PLOO", ]
#plot(owt_df02_gb09_wkly01a$ENTERO,
#     xlab = "Time",
#     ylab = "ENTERO Levels",
#     main = "ENTERO Levels Over Time: PLOO")
#grid()
print(acf(owt_df02_gb09_wkly01a$ENTERO, pl=TRUE, na.action = na.pass))
ggplot(owt_df02_gb09_wkly01a, aes(x=date_sample, y=ENTERO, group = 1)) +
  geom_line()
#scale_x_discrete(guide = guide_axis(check.overlap = TRUE))

owt_df02_gb07_wkly01a <- owt_df02_gb07_wkly[owt_df02_gb07_wkly$project == "PLOO" & owt_df02_gb07_wkly$depth_m_bin == "[0,8)", ]
#plot(owt_df02_gb07_wkly01a$ENTERO,
#     xlab = "Time",
#     ylab = "ENTERO Levels",
#     type = "o",
#     main = "ENTERO Levels Over Time: PLOO - [0,8)")
#grid()
print(acf(owt_df02_gb07_wkly01a$ENTERO, pl=TRUE, na.action = na.pass))
ggplot(owt_df02_gb07_wkly01a, aes(x=date_sample, y=ENTERO, group = 1)) +
  geom_line()
```

```{r}

```

