---
title: "Appendix A - ADS506-01-FA22 - Final Project"
author: "Team 1"
date: "12/05/2022"
output:
  html_document:
    df_print: paged
  pdf_document: default
header-includes:
- \usepackage{fvextra}
- \DefineVerbatimEnvironment{Highlighting}{Verbatim}{breaklines,commandchars=\\\{\}}
- \usepackage{pdflscape}
- \newcommand{\blandscape}{\begin{landscape}}
- \newcommand{\elandscape}{\end{landscape}}
---

## RMarkdown global setup
```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

```{r global.options, include=TRUE}
knitr::opts_chunk$set(fig.align = 'center')
```

```{r lib, message=FALSE, warning=FALSE}
library(AppliedPredictiveModeling)
library(BioStatR)
library(car)
library(caret)
library(class)
library(corrplot)
library(datasets)
library(e1071)
library(Hmisc)
library(mlbench)
library(gridExtra)
library(psych)
library(randomForest)
library(RANN)
library(reshape2)
library(rpart)
library(rpart.plot)
library(scales)
library(tidyverse)
library(tseries)
library(zoo)

set.seed(1699)
```

## Create function to generate boxplots for continuous variables
```{r}
# Define function to produce formatted boxplots
box_comp <- function(xcol = c(), df = NA, rtn_met = TRUE) {
  sig <- 3
  metrics_df01 <- data.frame(metric = c("",
                                        "Total N:",
                                        "Count",
                                        "NA Count",
                                        "Mean",
                                        "Median",
                                        "Standard Deviation",
                                        "Variance",
                                        "Range",
                                        "Min",
                                        "Max",
                                        "25th Percentile",
                                        "75th Percentile",
                                        "Subset w/o Outliers:",
                                        "Count",
                                        "%",
                                        "Outlier %",
                                        "NA Count",
                                        "Mean",
                                        "Median",
                                        "Standard Deviation",
                                        "Variance",
                                        "Range",
                                        "Min",
                                        "Max"
                                        ))
  for (var in xcol) {
    df_s1 <- df[, var]
    df_s1s1 <-data.frame(df_s1)
    df_s1_fit <- preProcess(df_s1s1,
                            method = c("center", "scale"))
    df_s1_trans <- predict(df_s1_fit, df_s1s1)
    

    # Calculate quartiles
    var_iqr_lim <- IQR(df_s1) * 1.5
    var_q1 <- quantile(df_s1, probs = c(.25))
    var_otlow <- var_q1 - var_iqr_lim
    var_q3 <- quantile(df_s1, probs = c(.75))
    var_othigh <- var_q3 + var_iqr_lim
    
    # Subset non-outlier data 
    var_non_otlr_df01 <- subset(df, (abs(df_s1_trans) <= 3))
    #var_non_otlr_df01 <- subset(df, (df_s1 > var_otlow & df_s1 < var_othigh))
    df_s2 <- var_non_otlr_df01[, var]

    # Begin calculating measures of centrality & dispersion
    var_mean <- mean(df_s1)
    var_non_otlr_df01_trunc_mean <- mean(df_s2)
    var_med <- median(df_s1)
    var_non_otlr_df01_trunc_med <- median(df_s2)
    var_mode <- mode(df_s1)
    var_non_otlr_df01_trunc_mode <- mode(df_s2)
    var_stde <- sd(df_s1)
    var_non_otlr_df01_trunc_stde <- sd(df_s2)
    var_vari <- var(df_s1)
    var_non_otlr_df01_trunc_vari <- var(df_s2)
    var01_min <- min(df[, var])
    var01_max <- max(df[, var])
    var01_range <- var01_max - var01_min
    var02_min <- min(var_non_otlr_df01[, var])
    var02_max <- max(var_non_otlr_df01[, var])
    var02_range <- var02_max - var02_min
    
    # Configure y-axis min & max to sync graphs
    plot_min <- min(var01_min, var02_min)
    plot_max <- max(var01_max, var02_max)
    nonoutlier_perc <- round((as.numeric(dim(var_non_otlr_df01)[1] / as.numeric(dim(df)[1]))) * 100, 1)
    # Fill in metrics table
    measure_val01 <- c(paste0("Variable: ", var),
                       "",
                       as.character(dim(df)[1]),
                       sum(is.na(df_s1)),
                       round(var_mean, sig),
                       round(var_med, sig),
                       round(var_stde, sig),
                       round(var_vari, sig),
                       round(var01_range, sig),
                       round(var01_min, sig),
                       round(var01_max, sig),
                       round(var_q1, sig),
                       round(var_q3, sig),
                       "",
                       as.character(dim(var_non_otlr_df01)[1]),
                       paste0(nonoutlier_perc, "%"),
                       paste0(round(100 - nonoutlier_perc, 1), "%"),
                       sum(is.na(df_s2)),
                       round(var_non_otlr_df01_trunc_mean, sig),
                       round(var_non_otlr_df01_trunc_med, sig),
                       round(var_non_otlr_df01_trunc_stde, sig),
                       round(var_non_otlr_df01_trunc_vari, sig),
                       round(var02_range, sig),
                       round(var02_min, sig),
                       round(var02_max, sig)
                       )
    
    var_name <- paste0("Variable: ", var)
    metrics_df01[, ncol(metrics_df01) + 1] <- measure_val01
  }
  # Format boxplot titles based on number of plots 
  if(length(xcol == 1)) { 
    boxplot(df, 
            ylab = "Parameter Values", 
            main = paste0("Boxplot for ", xcol, " (", grph_title, ")")) } 
  else { 
    boxplot(df,
            ylab="ParameterValues", 
            main=paste0("BoxplotforMultipleParameters","(",grph_title,")")) 
  } 
  #Returnandprintmetricstable(s) 
  if(rtn_met==TRUE){
    print(metrics_df01) 
    return(metrics_df01) 
    } 
  }
```

## Importing Train/Test Datasets
```{r}
# Import 4 separate CSV files
owt_df01a <- read.csv("water_quality_1990_1999_datasd.csv", 
                      header = TRUE, sep = ",")
owt_df01b <- read.csv("water_quality_2000_2010_datasd.csv", 
                      header = TRUE, sep = ",")
owt_df01c <- read.csv("water_quality_2011_2019_datasd.csv", 
                      header = TRUE, sep = ",")
owt_df01d <- read.csv("water_quality_2020_2021_datasd.csv", 
                      header = TRUE, sep = ",")

# Merge 4 seperate dataframes into 1
owt_df01 <- rbind(owt_df01a, owt_df01b, owt_df01c, owt_df01d)

print(head(owt_df01))
#describe(owt_df01)

#write.csv(owt_df01, "../data/Ocean Water/ocean_df01.csv")
```
## FActorize and format column types; print NA counts
```{r}
#Listofparametervalues 
param_lst01<-c("CHLOROPHYLL", "DENSITY", "DO", "ENTERO", "FECAL", 
               "OG", "PH", "SALINITY", "SUSO", "TEMP", "TOTAL", "XMS") 

#Listofcolnames 
col_lst01<-c("sample", "station", "date_sample", "time", "project", 
             "parameter", "qualifier", "units") 

#Citation:https://www.geeksforgeeks.org/find-columns-and-rows-with-na-in-r-dataframe/ 
owt_df02<-owt_df01 

for(c in col_lst01){ 
  owt_df02[,c]<-as.factor(owt_df02[,c]) 
}

#Generate NA summary tables 
#Citation:https://www.geeksforgeeks.org/replace-character-value-with-na-in-r/
owt_df02[owt_df02==""]<-NA 
print(head(owt_df02))
```

```{r}
owt_df02_na<-sapply(owt_df02,function(x)sum(is.na(x)))

owt_df02_notna<-sapply(owt_df02,function(x)sum(!is.na(x))) 

owt_df02_tbl01<-rbind(owt_df02_notna, owt_df02_na) 

owt_df02_tbl02<-rbind(owt_df02_tbl01, 
                      round(prop.table(owt_df02_tbl01, margin=2), 4)) 

print("Allparameters")
```
```{r}
print(owt_df02_tbl02)
```
```{r}
owt_df02a<-owt_df02[which(is.na(owt_df02),arr.ind=TRUE),] 
#print(head(owt_df02a))

for(p in param_lst01){
  df=owt_df02[owt_df02$parameter==p,] 
  #print(head(df[which(is.na(df$value),arr.ind=TRUE),])) 
  df_na<-sapply(df,function(x)sum(is.na(x))) 
  df_notna<-sapply(df,function(x)sum(!is.na(x))) 
  df_tbl01<-rbind(df_notna,df_na) 
  df_tbl02<-rbind(df_tbl01,round(prop.table(df_tbl01,margin=2),4))
  rownames(df_tbl02)<-c("NotNAn","NAn","NotNA%","NA%") 
  #print(p)
  #print(df_tbl02)
  #Thistablew/nullcountsandproportionsforeachfeaturenot displayedforspacepurposes→ 
}
```

## Bin depth_m variable

```{r}
owt_df02$date_sample<-as.Date(owt_df02$date_sample,"%Y-%m-%d") 
#Createbinsfordepth_mvalues 
depth_lvls01<-c("[0,8)", "[8,33)", "[33,47)", "[47,70)", "[70,90)", 
                "[90,112)", "[112,120]", "Unknown") 

#Plotdistributionofdepth_mvalues #Citation: https://community.rstudio.com/t/ggplot-x-axis-y-axis-ticks-labels-breaks-and-limits/119123/2→ 

ggplot(owt_df02,aes(x=depth_m))+ 
  geom_histogram(color="black", bins=40,aes(y=stat(density)))+ 
  geom_density(col="blue")+ labs(title="Histogram of`depth_m`Feature")+
  scale_x_continuous(breaks=seq(0,120,1))+ 
  theme(plot.title=element_text(hjust=0.5,size=12))
```

```{r}
#Createnewcolumnwithbins 
#Citation: https://www.marsja.se/r-add-column-to-dataframe-based-on-other-columns-conditions-dplyr/→ 
owt_df02<-mutate(owt_df02,depth_m_bin=case_when(depth_m<8~"[0,8)", 
                                                depth_m<33~"[8,33)", 
                                                depth_m<47~"[33,47)", 
                                                depth_m<70~"[47,70)", 
                                                depth_m<90~"[70,90)", 
                                                depth_m<112~"[90,112)", 
                                                depth_m>=112~"[112,120]")) 
#ReplaceNAswith"Unknown" 
#Citation:https://statisticsglobe.com/r-replace-na-with-0/ 
owt_df02$depth_m_bin<-replace_na(owt_df02$depth_m_bin,"Unknown")

#Citation:https://www.statology.org/order-bars-ggplot2-bar-chart/ 
owt_df02$depth_m_bin_factr=factor(owt_df02$depth_m_bin,levels=depth_lvls01) 
print(head(owt_df02))
```

```{r}
#Display transformed barchart 
ggplot(owt_df02,aes(x=depth_m_bin_factr))+ 
  geom_bar()+ labs(title="Barof`depth_m_bin`Feature")+
  theme(plot.title=element_text(hjust=0.5,size=12))
```

## Perform several aggregations on the data for performing EDA at multiple levels

```{r}
#Display aggregations by different features:
  # Station grouping = owt_df02_gb01
owt_df02_gb01<-owt_df02%>% 
  group_by(station)%>% 
  summarise(Count=n()) 
print(owt_df02_gb01[owt_df02_gb01$Count==min(owt_df02_gb01$Count),])
print(owt_df02_gb01[owt_df02_gb01$Count==max(owt_df02_gb01$Count),])
```

```{r}
# Project grouping: owt_df02_gb02 
owt_df02_gb02<-owt_df02 %>% 
  group_by(project) %>% 
  summarise(Count=n()) 

# Date_sample grouping: owt_df02_gb03
owt_df02_gb03<-owt_df02%>% 
  group_by(date_sample)%>% 
  summarise(Count=n()) 

#MainDF1 (owt_df02_gb04 Date and Paramter grouping)
owt_df02_gb04<-owt_df02%>% 
  group_by(date_sample,parameter)%>% 
  summarise(Avg=mean(value))
```
```{r}
# Paramter count group = owt_df02_gb05
owt_df02_gb05<-owt_df02 %>% 
  group_by(parameter)%>% 
  summarise(Count=n()) 

# depth_m grouping owt_df02_gb06
owt_df02_gb06<-owt_df02%>% 
  group_by(depth_m)%>% 
  summarise(Count=n()) 

#MainDF3:
  # owt_df02_gb07 = date_sample, project, depth bin, parameter groupings by avg
owt_df02_gb07<-owt_df02%>% 
  group_by(date_sample, project, depth_m_bin, parameter)%>% 
  summarise(Avg=mean(value))
```
```{r}
# owt_df02_gb08 depth bin groupings vy count
owt_df02_gb08<-owt_df02%>% 
  group_by(depth_m_bin)%>% 
  summarise(Count=n()) 

#MainDF2 
  # owt_df02_gb09= date, project, paramter groupings vy average
owt_df02_gb09<-owt_df02%>% 
  group_by(date_sample, project, parameter)%>% 
  summarise(Avg=mean(value))
```
## putting parameters into own columns via mutate:
```{r}
# putting paramters into columns via mutate:
  # citation: https://stackoverflow.com/questions/55516010/make-one-column-into-multiple-columns-in-r
split_try <- owt_df02_gb07 %>%
  mutate(rn=row_number()) %>%
  spread(parameter, Avg) %>%
  select(-rn)

head(split_try, 5)
```

```{r}
# dropping the TOTAL column as that was vague parameter
split_try <- data.frame(split_try)
splitted <- subset(split_try, select = -c(TOTAL))
#head(splitted, 3)


```
```{r}
sapply(splitted, function(x) sum(is.na(x)))
```
### PLotting histograms to see skewness/distribution
```{r}
# chlorophyll
ggplot(splitted, aes(x= CHLOROPHYLL)) +
  geom_histogram(aes(color= project, fill= project),
                 position= "identity", bins=7, alpha=.4) +
  labs(title= "CHLOROPHYLL (ug/L) Distribution per Project")
  # skewed with most obs towards left (low values)

# density
ggplot(splitted, aes(x= DENSITY)) +
  geom_histogram(aes(color= project, fill= project),
                 position= "identity", bins=7, alpha=.4) +
  labs(title= "DENSITY (sigma-t) Distribution per Project")
  # relatively normal distributed

# DO
ggplot(splitted, aes(x= DO)) +
  geom_histogram(aes(color= project, fill= project),
                 position= "identity", bins=7, alpha=.4) +
  labs(title= "DO (Dissolved Oxygen; mg/L) Distribution per Project")
  # relatively normal distributed

# ENTERO
ggplot(splitted, aes(x= ENTERO)) +
  geom_histogram(aes(color= project, fill= project),
                 position= "identity", bins=7, alpha=.4) +
  labs(title= "ENTERO (cfu/100mL) Distribution per Project")
  # skewed with most obs towards left (low values)

# FECAL
ggplot(splitted, aes(x= FECAL)) +
  geom_histogram(aes(color= project, fill= project),
                 position= "identity", bins=7, alpha=.4) +
  labs(title= "FECAL (cfu/100mL) Distribution per Project")
  # skewed with most obs towards left (low values)

# OG
ggplot(splitted, aes(x= OG)) +
  geom_histogram(aes(color= project, fill= project),
                 position= "identity", bins=7, alpha=.4) +
  labs(title= "OG Distribution per Project")
  # skewed with most obs towards left (low values)

# PH
ggplot(splitted, aes(x= PH)) +
  geom_histogram(aes(color= project, fill= project),
                 position= "identity", bins=7, alpha=.4) +
  labs(title= "pH Distribution per Project")
  # near normal distribution, slightly stronger drop off on alkaline side

# SALINITY
ggplot(splitted, aes(x= SALINITY)) +
  geom_histogram(aes(color= project, fill= project),
                 position= "identity", bins=7, alpha=.4) +
  labs(title= "SALINITY (ppt) Distribution per Project")
    # essentially only values between 30 and 40, not interesting

# SUSO
ggplot(splitted, aes(x= SUSO)) +
  geom_histogram(aes(color= project, fill= project),
                 position= "identity", bins=7, alpha=.4) +
  labs(title= "SUSO (cfu/100mL) Distribution per Project")
  # skewed with most obs towards left (low values)

# TEMP
ggplot(splitted, aes(x= TEMP)) +
  geom_histogram(aes(color= project, fill= project),
                 position= "identity", bins=7, alpha=.4) +
  labs(title= "TEMP (C) Distribution per Project")
  # near normal distribution

# XMS
ggplot(splitted, aes(x= XMS)) +
  geom_histogram(aes(color= project, fill= project),
                 position= "identity", bins=7, alpha=.4) +
  labs(title= "XMS Distribution per Project")
  # skewed to right with most obs for 50-100%, especially >75%

# Entero, fecal, OG, salinity, and arguably, XMS do not have interesting distributions. 
  # I think we can safely not do salinity and XMS since they are so uniform. 
# Entero, fecal, and Suso are measures relating to bacteria that often come from fecal matter and fecal matter (fecal) so they are likely going to show the same thing (modeling-wise). 
  # I think we should pick one (Suso has most diverse histogram) of the three.

```

### Summary (Descriptive Stats) with NA's included:

```{r}
summary(splitted)
```

### Plotting boxplots to see distribution

```{r}
# chlorophyll
ggplot(splitted, aes(x= CHLOROPHYLL, fill=project)) +
  geom_boxplot() +
  labs(title= "CHLOROPHYLL (ug/L) Distribution per Project")
  # primarily outlier filled

# density
ggplot(splitted, aes(x= DENSITY, fill=project)) +
  geom_boxplot() +
  labs(title= "DENSITY (sigma-t) Distribution per Project")
  # most outliers on low density measures

# DO
ggplot(splitted, aes(x= DO, fill=project)) +
  geom_boxplot() +
  labs(title= "DO (Dissolved Oxygen; mg/L) Distribution per Project")
  # very few outliers

# ENTERO
ggplot(splitted, aes(x= ENTERO, fill=project)) +
  geom_boxplot() +
  labs(title= "ENTERO (cfu/100mL) Distribution per Project")
  # the plot is essentially all outliers 

# FECAL
ggplot(splitted, aes(x= FECAL, fill=project)) +
  geom_boxplot() +
  labs(title= "FECAL (cfu/100mL) Distribution per Project")
  # the plot is essentially all outliers

# OG
ggplot(splitted, aes(x= OG, fill=project)) +
  geom_boxplot() +
  labs(title= "OG Distribution per Project")
  # the plot is essentially all outliers

# PH
ggplot(splitted, aes(x= PH, fill=project)) +
  geom_boxplot() +
  labs(title= "pH Distribution per Project")
  # more outliers on the acidic (low value) end more than alkaline end

# SALINITY
ggplot(splitted, aes(x= SALINITY, fill=project)) +
  geom_boxplot() +
  labs(title= "SALINITY (ppt) Distribution per Project")
    # the plot is essentially all outliers

# SUSO
ggplot(splitted, aes(x= SUSO, fill=project)) +
  geom_boxplot() +
  labs(title= "SUSO (cfu/100mL) Distribution per Project")
  # the plot is essentially all outliers, 
    # fewer than other bacterial measures (fecal, entero)

# TEMP
ggplot(splitted, aes(x= TEMP, fill=project)) +
  geom_boxplot() +
  labs(title= "TEMP (C) Distribution per Project")
  # some outliers, primarily at warmer temperatures

# XMS
ggplot(splitted, aes(x= XMS, fill=project)) +
  geom_boxplot() +
  labs(title= "XMS Distribution per Project")
  # primarily outliers

# Again the fecal, entero, OG, and salinity look nearly identical and equally uninteresting

```
